\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cAriel{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cSlave}{
  \nickname{Aldric}
  \mapnickinformal
}
You are \cAriel{}, former \cAriel{\Prince} of \pAtlantis{}, and current \cAriel{\Prince} of \pAmerica{}. You traded your old life away for a chance at love, and now seek to reclaim what you once lost.

Born as the mermaid \cAriel{\prince} of \pAtlantis{} to your \cKing{\parent}, \cKing{\King} \cKing{} and your \cQueen{\parent}, \cQueen{\King} \cQueen{}, your early childhood was a happy one. Your family doted on you, and you were a \cAriel{\prince} - loved by all, and without a care in the world. You loved your little \cPrincess{\sibling} \cPrincess{} from the moment she was born - and for a short time, you were one big, happy family.

That changed abruptly, however, when your \cQueen{\parent} disappeared when you were only 9 years old. The realization that one of your parents was well and truly gone left an unmistakeable hole in your life. Had \cQueen{\they} really loved you? Had \cQueen{\they} left \emph{because} of you? At some level, you knew that these thoughts were ridiculous. At another level, you couldn't get them out of your head.

You started to pull away from your family, from your duties, and distance yourself from them. You couldn't be fully invested here anymore - something had changed. It didn't take long for you to express your restlessness by joining the Explorer's Guild, led by your \cPlant{\Uncle} \cPlant{}. Here, at least, there was a bit of escape. Here, they didn't treat you like a \cAriel{\prince}. Here, you could explore, carefree, and find yourself even as you found treasures in the ruins. It was the perfect escape. You even met your first commoner friend - \cPriest{}, a \cPriest{\priest} of the Church of the Tides. Together, you had many adventures under the sea, and the hole in you heart filled, just a little.

Years passed in relative stability. The memories of your \cQueen{\parent}'s abandonment had all but faded from your mind. It was just a routine exploration - one like any other - when your life changed once again. Alone on an adventure for once, you noticed a ship passing by far above, and against your better judgment, you rose to the surface to see. Upon that ship, high above the waves, you saw a human so blindingly \cEric{\hot} that you nearly choked yourself staring at \cEric{\them} in the open air. It was at that moment that you knew what was missing in your life up until then. You had been born a \cAriel{\mer} when your destiny all along had been to be a human.

The next few days were a blur. You were in a haze of memory so deep and impenetrable that you weren't quite sure HOW you came to be standing in front of \cWitch{}, one of the most dangerous and powerful magicians beneath the sea. But the sight of \cWitch{\them} in all of \cWitch{\their} splendor soon broke you from your reverie.

You haggled for what seemed like an age, until finally, you came to an agreement. You would trade the promise of your firstborn \cArielsSon{\offspring}, to \cWitch{\them} for the illicit sorcery necessary for your chance at legs - and your chance at love. Satisfied, with only a niggling doubt left in the back of your mind, you accepted - and began the transformation.






Unfortunately for you, your success in wooing \cEric{} infuriated \cWitch{}, and \cWitch{\they} boiled up out of the ocean in an attempt to destroy you. Together, you, \cEric{} and \cEric{}'s \cPrince{\sibling} \cSlave{} defeated \cWitch{\them} at a heavy price, paying for her death with \cSlave{}'s life. Or so you thought.

Life on land went on though, and you and you and \cEric{} were married. With \cWitch{} dead, you had no fear for your possible children. You had a \cWillow{\offspring} a year later. On land you also learned that a cure exists for \cPolio{}. This crippling disease had begun to affect your merkin in the years before you left. The disease was not yet an epidemic when you left, but there was always that chance, since merfolk had no way to combat it. You worried about your homesea, but you were happy on land.

Well, except for the part where your \cKing{\parent} wont speak to you any more. \cKing{\They} forced you to cut ties with your entire family when you left the sea by disowning you. You miss them, but the happy family you remember from your childhood years was gone long before you left, lost along with your \cAthena{\parent} when you were 9. At least with \cEric{} you have a family with a \cEric{\parent} that didn't sink into endless depression. \cEric{} is there for \cWillow{} in a way that \cKing{} was {\bf never} there for you.

Despite being human, you retained your ability to communicate with ocean creatures. A few years ago, a seagull turned up outside your window with a fish in it's mouth. The fish relayed an urgent message from your contacts in \pAtlantis{}. (Despite your \cKing{\parent}'s best attempts to isolate you for the ``sake of \pAtlantis{}'', you had non-merfolk friends who still kept in touch) Word in the underground was that \cWitch{} had surfaced again, in disguise of course.  Suddenly the promise of your firstborn \cArielsSon{\offspring} stirred in you uneasily. It was nothing like the pleasant sensation of \cArielsSon{} kicking in the womb. Yes, you were pregnant again, this time with a \cArielsSon{\offspring}.

You immediately went to \cEric{} and discussed what to do. The two of you agreed that you would have to return to the ocean temporarily, to try to confirm these rumors, and maybe find some way out of your contract if it turned out to be true that \cWitch{} was still alive. You reached out to your \cKing{\parent}, apologized a thousand times to him, and begged for permission to attend the \cExExKing{} Ball this year. \cKing{\They} eventually relented, but only after you agreed to bring \cWillow{}, despite the danger. \cKing{} wanted to meet his grand\cWillow{\offspring} and you couldn't fault \cKing{\them} for that. Rather than reveal that it would be incredibly dangerous to bring \cWillow{}, you agreed. If your \cKing{\parent} knew what you had signed away in order to become human, you might 



\end{document}

