\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cAthena{}}

\bigquote{``Her power has been made to derive from her sexuality. It has always been preferable to attribute a woman's success to her beauty rather than to her brains, to reduce her to the sum of her sex life.''}{--Stacy Schiff}

Your name is \cAthena{}. Well, actually it is \cQueen{}, but everyone who knew you by that name thinks you are dead.

You are from \pAtlantis{}. You think. You are not sure, but you look much more like an \pAtlantis{}n than a \pPacifica{}n mer\cAthena{\human{}}. Unfortunately your earliest memories are of the barren rooms and harsh teachers of \pAssassin{}, hidden deep in the icy waters of the Bering Strait. You have no idea where you were born, or how you ended up in that dreadful place. 

Wait, no. Your earliest memories are of growing up with a loving family on a coral plantation in the Caribbean. -- Aren't they?

You shake your head, as if to dislodge the false memories. It's been like this for years, getting worse all the time. False memories, implanted in your mind to make you a sleeper agent, bleeding into memories of your real life. It doesn't help that you often wish that the false memories were true. You had a much gentler pretend life. If only you could have lived that one instead of the one you did.

For ten years you trained at \pAssassin{}, until you were ready. Ready to kill \cKing{\King} \cKing{}. You learned a hundred ways to kill a merman with weapons, and a hundred more ways to do it bare handed. But you were more than just an assassin. You were trained in the arts as well. Raised to impersonate a mer\cAthena{\human} of the highest station. It was your job to infiltrate \pAtlantis{}, and the heart of the \cKing{\King}, and to strike \cKing{\them} down when \pAtlantis{} least suspected. You were to be the final nail in the coffin of this treacherous nation.

To ensure a seamless integration into \pAtlantis{}n society, your memories were locked away, and a false childhood implanted in your mind. You were left on a destroyed coral plantation, within the ransacked realm of a minor noble, for an \pAtlantis{}n patrol to find. You were whisked off to the capital since everyone, including you, was fooled into believing you were the only living heir to the Baron's lands due to a necklace bearing his seal found on your person. Your training served you well via the subconscious, and you quickly rose to prominence at court, and became a favorite of young \cKing{\King} \cKing{}. You would often accompany \cKing{\them} on the long walk to the royal cemetery, where \cKing{\they} went almost daily. You listened with sympathy to the ails of \cKing{\their} heart, and it was with much joy and hope that you accepted \cKing{\King} \cKing{}'s marriage proposal at the end of \cKing{\their} year of mourning.

\cKing{\King} \cKing{} was almost always distant and melancholy. Even the birth of your fourth child could not stir \cKing{\them} to joy, almost 10 years after the tragedy that put \cKing{\them} on the throne. Only music ever brought a smile to \cKing{\their} face. The lively music and dance of the polka reached a part of \cKing{\them} that not even the pain \cKing{\they} had endured could destroy. \cKing{\They} smiled, and laughed - \cKing{\They} lived - when \cKing{\they} was on the dance floor.

About a year later, a nixie came to you in a dream, begging you to journey to \cNixie{\them} home. She warned you of impending threats to \pAtlantis{} and offered you a \iMusicBox{\MYname} to protect your country. Some people wouldn't have understood why this was such a big deal, but you did. Music is magic, or the preservation of it anyway. Music has the power to remember spells, and to extend their duration far beyond what would ordinarily be possible. A spell of protection might only last a few days, unless laced into a melody, in which case a well cast spell could endure for years. Too bad you have never demonstrated a proclivity for magic. Even if it is essencially banned in \pAtlantis{}, you've always felt that it still has its uses. 

What else could you do? \cKing{} had given so much for \pAtlantis{}, surely you could sacrifice a few weeks away from home to protect your beloved homeland. You journeyed far to the north, to the fjords of Norway, where you met a nixie of great power, \cNixie{\MYname}, in the brackish water where \cNixie{\them} stream joined the sea. \cNixie{} gave you a magical music box. Wound once every decade, it played a song that would protect \pAtlantis{} from a number of dangers that \cNixie{} had seen portents for. \cNixie{\They} showed you how to wind it with a special key on a gold chain that she also bestowed upon you. You vowed never to take the key from around your neck as long as you should live. You agreed to pass the secret on to one of your daughters when the time was right. You returned to \pAtlantis{}, flush with triumph.

All your hopes and dreams were shattered about a week later however, when you woke up in the middle of the night, the truth about your past pouring through your head. You knew suddenly that you were not a gentle mer\cAthena{\human} of \pAtlantis{}, but a spy and an assassin sent to kill \cKing{\King} \cKing{}.

You balked at the horror of your task - to kill your beloved. Rather than complete your mission, you staged your own kidnapping that very night and fled \pAtlantis{}. You weren't able to tell anyone what had happened, you didn't even get to kiss your youngest daughter, \cDaughter{} goodbye in her crib. But it was for their own safety that you did it. You had to leave as soon as possible. If \pAssassin{} could lock your memories away, maybe they could also mind control you. You couldn't risk that. So you swam.

Your heart was heavy with sadness and loneliness, and your mind was clouded with conflicting pasts. In your distracted state, you blundered into a fishing net set in the shallows and nearly drowned. It was only by happenstance that you survived. \cGeneral{\MYname{}}, a human General, was meditating on the beach nearby. Intrigued by the strange movements of the fishing net floats, he dove into the water and came to your rescue. 

You were terribly frightened of \cGeneral{\them}, despite the rescue. There is precious little that your real memories and your fake ones agree on, but one of the things they do agree on is that humans are at best dangerous. The only known interactions with merpeople are short, brutal, and never end well for merfolk. You wiggled free of his arms and dove into the water. It wasn't until you were almost 20 meters down that you realized that \cGeneral{} was keeping pace with you. \cGeneral{\They} wasn't human! \cGeneral{\They} was a mer\cGeneral{\human}! But you could have sworn you had seen legs when he freed you from the net and lifted you out of the water. What was going on? 

It turned out that \cGeneral{} was a shape-shifter. \cGeneral{\They} could change freely between being a human and a mer\cGeneral{\human}. \cGeneral{} didn't ask many questions about your past, but treated you with civility regardless. \cGeneral{\they} didn't even blink when you scrambled to come up with a name. It hadn't occured to you until he asked that you would have to leave the name \cQueen{} behind. You settled on \cAthena{}. Over the next few months, you returned regularly to his beach, and when \cGeneral{\they} agreed to abandon the shore and live with you under the waves, your heart sang.  \cGeneral{} has a family estate in the North Sea. Safely away from \pAtlantis{}, you began to relax, eventually fell in love, and married \cGeneral{}. You and \cGeneral{} celebrated your son's fifth birthday last month. 

Just when you thought you had put your past behind you, both the good and the bad, a letter arrived on the Fair Isle Current. It was anonymous, but casually dropped detailed, personal information about your past life in \pAtlantis{}. The letter went on to reveal a new assassination plot against \cKing{}, entreat you to return to \pAtlantis{}, and imply that no one else would be able to save \cKing{}. You simply \emph{must} return. It is not like you stopped loving \cKing{} really, just that circumstances had forced you apart and you had made the best of things with \cGeneral{}.

It will be incredibly dangerous to return to \pAtlantis{} however. \cKing{}, and in fact all of \pAtlantis{}, thinks you are dead. Should you be found out, you might be executed as an impostor, or a deserter(!).  There is also the matter of the \iMusicBox{\MYname}. It has been so long since you had a chance to wind the \iMusicBox{\MYname}. Tonight may be your only chance to pass the secret of the \iMusicBox{\MYname} on to one of your daughters.

\cGeneral{} insisted that the letter was little more than bait, but you had to go and see for yourself.  In the end, \cGeneral{} conceded to let you go, as long as he came with you. It was a simple matter to acquire a couple of tickets to tonight's gala; \cKing{} would be appalled to learn just how simple.  Upon arriving at the castle, you slipped away from the festivities to wander the old familiar halls for a while. It felt good to be home. You went to the royal treasury to see the \iMusicBox{\MYname}, only to discover that it was missing! \pAtlantis{} seems to be beset with dangers. Tonight is going to be a stressful and precarious dance with unknown and dangerous partners, and the fate of \pAtlantis{} hanging in the balance.


\begin{itemz}[Goals]
  \item Find the \iMusicBox{}, wind it up and put it back on display.
  \item Pass the secret of the \iMusicBox{} on to \cAriel{} or \cDaughter{}.
  \item Foil the assassination attempt against \cKing{}.
  \item Avoid being discovered as \cQueen{\King} \cQueen{}.
\end{itemz}


\begin{itemz}[Notes]
  \item \pAtlantis{} has a long tradition of Polka dancing. If you do not know how to polka, please let a GM know as soon as possible.
  \item You have a tattoo on your left bicep that marks you as an assassin from \pAssassin{}. All students of the school have the same tattoo, in the same place. See a GM to acquire a temporary tattoo before game.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cKing{}} Your former \cKing{\spouse{}}.
  \contact{\cGeneral{}} Your current  \cGeneral{\spouse{}}. This could get awkward if you are discovered.
  \contact{\cAriel{}} Your eldest daughter.
  \contact{\cDaughter{}} Your youngest daughter
\end{contacts}


\end{document}

