\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cBodyguard{}}

Your name is \cBodyguard{}. You have been \cPrince{}'s bodyguard for three years. You take pleasure in a job well done, and have foiled half a dozen assassination attempts since you signed on, thanks in no small part to your magical training.

You were born in the mid-pacific mountains to a loving, and very lucky family. You were the younger of two chidren - a very rare thing in \pPacifica{}. Children are rare in \pPacifica{}, two in a family is almost unheard of. Your older \cSpy{\sibling} \cSpy{} and you got along quite well, at least as far as you remember. You were five when \cSpy{\they} disappeared. 

You grew up fairly normal, attending school, playing with the few other neighborhood children - nothing dramatic. You did start taking lessons from the local magician at the age of 13, once your powers really started to come into their own. Unfortunately, it was not really soon enough.  You had accidentally cursed your mother when your powers spiraled out of control in the middle of a nightmare. So maybe your childhood had not been so normal...

On your 16th birthday, your \cSpy{\sibling} turned up on your family's doorstep with a harrowing tale of having been kidnapped by the black market trade, running away from her new family and journeying along across much of the Pacific ocean to return home. You were so glad \cSpy{\they} was home. \cSpy{\They} quickly went off to be a diplomat though, and you rarely see \cSpy{\them} these days.

Once you graduated from high school, you had no desire for higher education. School was stuffy, boring, and all together too hard. You turned instead to the \pPacifica{}n military, where hard work paid off quickly with promotions and bonuses. For some reason, your \cSpy{\sibling} never liked your decision. You enjoyed the military, and were crushed when your superiors transfered you to bodyguard training after a minor scuffle.

Not one to give up though, you made the bestof it, and soon found that bodyguard training was not as bad as you had thought. You weren't assigned to any stupid nobles or anything, and in fact were soon in charge of training the new recruits yourself. Some 10 years into your career though, the \cPacificanRuler{\King} \cPacificanRuler{\them}self summoned you and assigned you to guard \cPacificanRuler{\them} \cPrince{\offspring} \cPrince{}.

\cPrince{} turned out to be a reasonable \cPrince{\guy}, who gave you a lot of freedom to do your job your way. This worked out well, because it gave you plenty of free time to pursue your magical talents and develop your own potion that would allow you to better protect and defend him.

When \cPrince{} was selected to go to \pAtlantis{} in order to try to secure a treaty, you of course began packing your bags. Despite not knowing much about \pAtlantis{}, you were happy to go for a number of reasons. In the midst of preparations you were approached the court magician. He entreated you to carry a message to the Magician's guild of \pAtlantis{}.  Their guild has been in hiding for about 15 years, ever since the \cKing{\King} banned most forms of magic in \pAtlantis{}. It is imperative that you re-establish contact with them, and learn what they have been up to. Without this contact, the guild is but half it's original size, and the flow of information and new magical research has all but dried up.

On a more personal note, \pAtlantis{} may offer your last hope for a child of your own.  You've tried everything to get this child. But even with magical assistance, you and your \cVHusband{\spouse} have been unable to conceive. Your \cVHusband{\spouse} wouldn't like that you are considering a black market child. Even you are a little surprised at how much power the idea has over you. After all, your \cSpy{\sibling} was a victim \cSpy{\them}self. But the allure of having children is so strong.  You are sure you can convince your \cVHusband{\spouse} to accept the child once you have it with you.  Conveniently enough, the clergy in \pAtlantis{} are rumored to be suppliers of \pAtlantis{}n children. And they often sell the children for much cheaper than you could get in \pPacifica{} because there are more available.

Lastly, and and of national importance, there have been rumors for several months of Indian aggression. There is very little said overtly, and whenever it is, \cPrince{} quickly stomps it out as idle speculation. You are not convinced it is unimportant however. Your training has given you almost a 6th sense about when not to dismiss seemingly trivial details.  You have to find out more about this. The sooner you have proof, the sooner you will be able to convince \cPrince{} to begin preparations. \pPacifica{} can't afford to be caught unaware if \pIndia{} attacks.  If you complete this tonight, which you hope an infusion of \pAtlantis{}n intelligence can help you do, you may even be able to persuade \cPrince{} to enlist \pAtlantis{} as a military ally.

In preparation for your trip, you sequestered yourself for 48 hours and performed the incredibly draining foresight spell. At first you saw nothing alarming. There appeared to be little for Jared, which suits you just fine. But then, deep in the bowl of water, you watched someone you didn't recognize die. Tangled in this tragic scene were the threads of a young magician's power. You aren't sure if they are connected, but you can't take that risk. You need to find the young magician and take them under your wing as soon as possible. Without proper tutelage, magical powers can soon spiral out of control and become a huge danger to everyone nearby.

As you walked into the ball this evening, there was a crazy man floating by the door, telling a fairy tale about a \iWishingStone{\MYname}. You dismissed him at first, but the more you think about it, the more you wish it were true. Could it really hurt anything to go looking for it? You might even be able to cure your mother of the curse with the \iWishingStone{\MYname}.

\begin{itemz}[Goals]
  \item Re-establish contact with the Magician's Guild of \pAtlantis{}
  \item Find and induct the budding magician into the Magician's Guild, for their protection, and yours.
  \item Find a way to cure your mother
  \item Arrange to receive a black market child.
  \item Research the rumors of \pIndia{}n aggression.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cPrince{}} The \pPacifica{}n \cPrince{\Prince}, and your friend.
  \contact{\cSpy{}} Your \cSpy{\sibling}, who you trust implicitly.
  \contact{\cDiplomat{}} The diplomat in charge of the \pPacifica{}n delegation.
\end{contacts}

\end{document}
