\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cDiplomat{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\cQueen{\They} left you. \cQueen{\They} left you to rot. You turn the thought over in your mind, worrying it like a sore tooth. You shouldn't poke and prod at it, but it feels so good. The fire inside you burns hot.

You are \cDiplomat{}, a graduate of \pAssassin{} currently masquerading as a gifted diplomat. You and \cQueen{} were close friends who tried to run away together in your last year. Unfortunately, clever as the two of you were, the Guild was cleverer. The two of you were caught, and put on ``trial''. Being older than \cQueen{}, you were held almost entirely responsible for corrupting \cQueen{\them}. Ha! As if there was anything left to corrupt after 10 years in that miserable place. As punishment, you were put in suspended animation and held as collateral against \cQueen{}, while \cQueen{\they} went on her first mission. When \cQueen{} abandoned \cQueen{\them} mission however, the Guild did not kill you as threatened. Instead they bided their time, and left you suspended for many more years. Although suspended animation stops the aging process, it does not suspend the mind. Most people go crazy after even a few weeks of not being able to do anything but think. You were made of stronger stuff however, and you came through mostly unscathed.

\pAssassin{} finally brought you out of suspension, just 3 years ago. They fed your desperate hunger for news, revealing that \cQueen{} had abandoned \cQueen{\them} mission, and \cQueen{\them} dear friend, in order to go marry some fool of a General in the North Sea. You knew many years had passed, but surely you had not meant so little to \cQueen{} that \cQueen{\they} had forgotten about you. And yet, here was the proof.  

In the midst of your seething, the Guild offered you a chance for revenge.  \pAtlantis{} and \pPacifica{} had just recently begun peace talks. While peace is not an environment that \pAssassin{} normally approves of, \cPacificanRuler{\King} \cPacificanRuler{} is very much interested, and \pAssassin{} knows better than to upset \cPacificanRuler{\them}. They were therefore offering you a chance to become a diplomat, slip into \pAtlantis{} and kill \cQueen{}. To make the the deal irresistible, the Guild offered to nullify your obligation to them if you succeed at killing \cQueen{\them} undetected. You could be free to go start your own life, your own way, without \pAssassin{} or treacherous friends to ruin it.

So you became a Diplomat, after a few months of rehabilitation and updating your worldly knowledge.  \pAssassin{} placed you on the fast track, and you were soon the head diplomat on the project. 

Then fate stepped in. Cruel, sweet fate. You were in \pAtlantis{}, dancing the tiring dance of politics, pretending to care, pretending to be outraged on behalf of your country, etc, etc. You were so tired. So bored. So restless. You just wanted to get your hands on \cQueen{} and be done with this horrid, extended chapter in your life. But then, one late night, you were wandering the halls of the palace when you collided with an angel. \cPrincess{\They} was gorgeous. No, \cPrincess{\they} was perfect. You stared into \cPrincess{\them} eyes for a heartbeat, then two. You ran your fingers self consciously through your uncombed hair. You must look a mess, with bags under your eyes from too many late nights up pouring over documents.  You finally found your voice, and tried to stammer out an apology for the collision. Ever the graceful \cPrincess{\prince}, \cPrincess{\they} asked if you would join her in a stroll about the gardens. Somehow you managed to push the word ``yes'' out past your uncooperative lips. And the rest was, as they say, history.

Your angel was none other than \cPrincess{}, \cPrincess{\prince} of \pAtlantis{}. In that instant the pain and boredom of politics evaporated. You threw yourself into the proceedings with vigor. After all, without good faith between the countries, how could you ever hope to see \cPrincess{} on a regular basis? To your great frustration, politics move slowly. You couldn't see enough of \cPrincess{} to satisfy either of you. Then \cPrincess{\they} came up with a reckless, dangerous idea that you couldn't resist. \cPrincess{\They} managed to sneak across the border into \pPacifica{} to see you! It was the most glorious afternoon. No formal proceedings, no pretending to be nothing more than acquaintances. No trying to sneak off and snatch a few moments alone. It was dangerous. So dangerous. If \cPrincess{\they} were caught\ldots{} and then \cPrincess{\they} was.

\begin{itemz}[Goals]
  \item Kill \cQueen{}.
  \item See that the treaty is signed. Make sure it is as favorable to \pPacifica{} as possible.
  \item Acquire a glow shell as a sign of your devotion to \cPrincess{}.
  \item Find a way to convince \cKing{} to let you marry \cPrincess{}, otherwise elope with \cPrincess{}.
  \item Find a regal gift to bring back for \cPacificanRuler{}.
\end{itemz}

\begin{itemz}[Notes]
  \item You have a tattoo on your left bicep that marks you as an assassin from \pAssassin{}. All students of the school have the same tattoo, in the same place. See a GM to acquire a temporary tattoo before game.
\end{itemz}
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{}
\end{contacts}

\end{document}
