\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cManta{}}
\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}


Where to begin? The beginning is so far in the past, it's hard to trace the convoluted path that has led you to this day. You guess it all began with \cExExKing{\King} \cExExKing{}, \cExExKing{\King} \cKing{}'s grand\cExExKing{\parent}, and your \cExExKing{\parent}. Although can you really call \cExExKing{\them} your \cExExKing{\parent}? \cExExKing{\They} never accepted you, never acknowledged you, never did anything for you.

\cExExKing{\They} was jealous of \pPacifica{} in every way. From the bounty of the harvests on the Central Pacific Basin, to the beauty of the kingdom's only \cMother{\prince}, your \cMother{\parent} \cMother{\MYname}. \cExExKing{} started a war over it. A war that devastated both \pPacifica{} and \pAtlantis{}. In the end, he got what he wanted though. His aggressive military tactics led to a breech in the castle wall, and the successful capture of your \cMother{\parent}. \cExExKing{} carried \cMother{\them} off, back to \pAtlantis{}, and by the time a successful counterattack was mounted to retrieve her, you had already been conceived.

Your \cMother{\parent} burned for revenge. \cMother{\Them} brothers wished to just kill the child and pretend as though you had never been. But your \cMother{\parent} was cleverer than they could ever hope to be, and persuaded \cMother{\them} brothers to spare your life, but put out the word that you had died.

And so you were raised in secret, at \pAssassin{} where you and your \cMother{\parent} were hidden away. The only thing that grew faster and stronger than you was your hatred of \pAtlantis{} and what \cExExKing{} had done to your \cMother{\parent}. Although your \cMother{\parent}'s seer's gift pass only through the female line, you were not without your own talents. From a young age, magic flowed in your veins, and you studied hard from the moment you could read.

At the age of 14, you set out on a quest to find \iTrident{\MYname}. \cMother{} had a vision that the fate of both \pPacifica{} and \pAtlantis{} were intimately tied to it's fate, and despite your youth, you relished the chance to strike back at your \cExExKing{\parent}'s country. The search took you 20 years and seemed to be dogged by bitter tragedy. Your \cMother{\parent} died, alone, while you were fighting for your life in the freezing waters of the Ross Sea. In the end it turned out to be a bad lead anyway. Your intelligence next led you to Atlantis. With a few words whispered in the right ears, you persuaded \pPacifica{} to attack the Angola plain of \pAtlantis{} by sneaking through the neutral kingdom of \pIndia{}. The operation gave you the perfect cover as you blended in with a group of \pAtlantis{}n refugees. This time, the move almost paid off. You established yourself in court, and made your extensive magical powers available to the then current \cExKing{\King}, \cExKing{}. You rose through the ranks in court, as well as in the Magician's Guild. You were soon among those elected to the Court of Advisors, with easy access to the \cExKing{\King}s ear. This put you in the crucial position to continue your search for \iTrident{\MYname}.

You eventually traced the trail of  \iTrident{\MYname} to the fjords of Norway, and a nixie by the name of \cNixie{}. Unfortunately \cExKing{} got there first. He persuaded \cNixie{} to give him the \iTrident{\MYname}. You watched from a convenient cave as he swam away. You fantasized about blasting him out of the water with a particularly vicious spell, but with \iTrident{\MYname}, he would certainly have bested you in a fight.

You slunk back to \pAtlantis{}, and waited. You studied the problem from every angle, but there didn't seem to be a way around the problem of \iTrident{\MYname}. Then \cKing{} was born. Most would have despaired at that point, but you were a patient mer\cManta{\human}. Here was another chance to ruin \cExExKing{}'s line. You arranged to have a baby \pAtlantis{}n \cQueen{\kid} kidnapped and taken to the Assassins Guild. There \cQueen{\they} was raised and trained as the perfect match for \cKing{}. When \cKing{} was just old enough to take the throne, you smuggled a dozen \pPacifica{}n assassins into \pAtlantis{} to kill the royal family. \cKing{} was \emph{conveniently} off on an Explorer's Guild expedition. Again, many might question your logic -- why not have the assassins kill \cKing{} too? Your long game wasn't mature yet though. Proof of your lineage was frustratingly hard to come by with your mother and father both dead. You couldn't risk the kingship passing too far from the \cExExKing{} lineage, otherwise you might lose your claim to the throne.

Converted to a sleeper agent with a fairly complex memory suppression spell, you integrated \cQueen{\them} in the \pAtlantis{}n court.

While you secretly manipulated the young \cKing{\prince}'s life, you continued to tend your other plans. Among them was the Magician's Guild. You maintained your position as elected representative to the Court of Advisors, and cultivated your standing with other magicians. One particularly powerful contact was \cWitch{}. \cWitch{\They} gave you an anti-aging spell that if properly maintained meant you could essentially live forever. At the age of 52, you stopped aging.


%%Helped heal and hide ursula, knows about aldric

\begin{itemz}[Goals]
  \item Blah
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cKing{}} Your nephew and the man who is sitting on your throne.
\end{contacts}

\end{document}
