\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cPrince{}}

You are \cPrince{}, crown \cPrince{\Prince} of \pPacifica{} and heir to the throne. You rule your subjects with pride and want to protect them at all costs, which means getting this treaty signed above all else.

Born into opulence, you have enjoyed easy prosperity from an early age. Your \cPacificanRuler{\parent} \cPacificanRuler{\King} \cPacificanRuler{} doted on you, but to you, that attention seemed smothering. Lessons in the art of diplomacy were difficult and taxing, but you relished the challenge – so you didn't take kindly to your mother’s worried attentions after every single lesson. Without a strict guiding hand, you became rebellious, and spent the majority of your free time sneaking out into the surrounding town to mingle with your common friends, and to take part in the commoner’s practice of dancing. Your mother didn't approve, worrying that you would pick up a disease or worse, be kidnapped – but you paid her no mind. What was the worst that could happen to a royal \cPrince{Prince}, beloved by the people?

In retrospect, perhaps you should have listened to your \cPacificanRuler{\Parent}. It wasn't long before the plague hit your circle of friends. While \ppolio{} was rocking the lower quarters of the capital, you were rocked along with it, contracting a severe case. Your \cPacificanRuler{\Parent} immediately sequestered you and began treatment, but not before the disease took a heavy toll on your health. Upon emerging from the palace after being given a clean bill of health, you returned to the lower quarters. You fully took in the devastation, and a little part of you died that day. Friends you had known and danced with all of your life had died in the streets as you had been being fanned and pampered in your royal bedroom, oblivious that anyone other than yourself had been suffering. You resolved that day to do everything in your power to bring the cure to \pPacifica{}, and to champion the cause of the marginalized from then on.
%%Adriana actually brought this information 6 months ago
It didn’t take you long to find a way to make good on your vow, though you knew the way would be challenging. Your research revealed that \pAtlantis{} had the cure in abundance, and had all but eliminated \ppolio{}, a result of their friendly relations with the humans. Though you didn't like \pAtlantis{} or the humans any more than the next \pPacifica{}n, the cost in lives of this fight was only becoming higher. You gathered your political allies, constructed your arguments, and awaited your opportunity – and soon, it came, in the form of a wayward \cPrincess{\Prince}. \cPrincess{} was radiant as she was taken in for questioning, and not just because of the chance she represented. You immediately seized the opportunity to open talks with \pAtlantis{}, sending \cPrincess{\them} back unharmed as a gesture of good faith, and immediately began drafting the treaty that you would propose. Things moved quickly after that, and sooner than even you expected, the trip to \pAtlantis{} was scheduled. You would leave within the month as head of the delegation.

You couldn't let this opportunity go to waste, and as such, your objectives were clear. First and foremost, the treaty must be signed –- it would secure peace between your nations and, more importantly, the cure to \ppolio{}. If you were lucky, you could even secure the \cPrincess{\Prince}'s hand in marriage -– after all, a political marriage could strengthen the treaty. \cPrincess{\Them} beauty was just a side benefit, of course. You also had managed to arrange a meeting with the former \pAtlantis{}n \cAriel{\Prince}, \cAriel{} to obtain a sample of the \ppolio{} cure. You wouldn't feel right signing the treaty into law without verification that what you were bargaining for was real, and bringing it back would mean that your scientists could analyze it to determine its effectiveness.   

On a more personal note, your studies of \pAtlantis{} have engendered a certain curiosity in you about their native dance forms. You had grown up dancing the waltz, but have read that \pAtlantis{} practices a different form of dance altogether. You snuck a line into the treaty about creating a program for cultural exchange, and while it isn’t quite as important as an end to the war or the cure, you’d really like to see your countries come together culturally as well – starting with a dance lesson for the diplomats at the ball! If only you had a partner to help you teach\ldots

Upon reaching \pAtlantis{}, you immediately realized that something was strange. Why was there no music here? You were used to constant background music in \pPacifica{}, and hadn't thought that \pAtlantis{} would be any different. Something was up here, and you were quite curious as to what it was…

\begin{itemz}[Goals]
  \item Get a fair and balanced treaty signed at all costs
	\item Obtain a sample of the \ppolio{} cure to verify its potency
	\item Marry \cPrincess{} if at all possible, using the treaty if necessary.
	\item Promote your program of cultural exchange by teaching as many people to waltz as possible, and learning as many dance forms as you can
	\item Protect your delegation
	\item Find out what happened to the music!

\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cBodyguard{}} – your loyal bodyguard of 3 years, who harbors paranoid delusions about an impending invasion.
	\contact{\cDiplomat{}} – The head diplomat sent to help you get the treaty signed.
	\contact{\cSpy{}} – A second diplomat sent to aid in the signing of the treaty.
	\contact{\cAriel{}} – Former \cAriel{\Prince} of \pAtlantis{} who has the cure you're looking for.
	\contact{\cKing{}} – \cKing{\King} of \pAtlantis{} and a worth adversary.
	\contact{\cPrincess{}} – a beautiful princess who you hope to marry for \cPrincess{\them} beauty and political power.
\end{contacts}

\end{document}
