\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cWitch{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\bigquote{``Pearls before Swine''}

Beauty and Power. Those wonderful, tempting, wretched things. Beauty and Power have defined your entire life. They are liberation and confinement, the bait and trap, a gilded cage you couldn't resist.

You are the paragon of beauty, and have been for almost 60 years. As a young \cWtich{\mer}, you were the belle of your town. From the time you began to flower into \cWitch{\human}hood, until your 18th birthday, you were elevated as the most beautiful \cWitch{\mer} anyone had ever seen. Every year at the midsummer festival, you were crowned as \cWitch{\King} of the festival. You loved the attention and the flattery, and your ego grew uncontrollably.

On your 18th Birthday, the day of the midsummer festival, everything started to go wrong. You decided to get a reading from a quarent tucked away in a corner of the fair. You'd seen him in previous years, but had never worked up the courage to approach him. Your curiosity finally mastered your fear though, and you darted into the tent. Scents in the water, contained by the fabric of the tent and a fair bit of magic, assailed you. You felt light headed, and almost backed out, but you couldn't figure out where the door was. Actually, you couldn't remember why you were there at all until the old man asked you if you wanted a reading.

You nodded and settled shakily into a chair.

You are a powerful sorceress, out to claim your rightful place on the throne of \pAtlantis{}. 

You were one of \pAtlantis{} most powerful magicians until you were defeated by ariel and eric.  Well first you turned ariel human. Your contract traded this transformation for her first born son. If she fails to hold up her end of the deal, the spell will break and she will revert to being a mermaid. as the writer of the contract, you do have the discretion to declare an alternative payment acceptable. but this is her last chance. You want the child b/c it screws with the human kingdom and you hate them b/c they defeated you.

Despite this defeat, you did make off with one useful thing. Prince aldric. You cast 2 spells on him. One to prevent him from revealing who you are, and the other to make him your slave. He obeys your every

%%Knows manta's back story

\begin{itemz}[Goals]
  \item Blah
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{}
\end{contacts}

\end{document}
