\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cSlave{}}

You are a human \cSlave{\Prince} enslaved by an evil \cWitch{\magician} and diguised as a merman against your will.

Your early life was a happy one, being pampered as a \cSlave{\Prince} should in your castle in \pAmerica{}. Your relations with your older \cEric{\sibling} were good, and your father doted on you twice as much, since your mother was lost at sea during a family outing when you were just a boy. You took full advantage of this by wiling away your time, going through your lessons and flirting with the courtiers. You had a good life...

...a fact that changed abruptly on your 18th birthday when a monster attacked the palace.

It had been just a normal day for you. Your lessons in diplomacy were winding down and one of your favorite courtiers wanted to share dinner with you. The stage had just been set for a pleasant evening when shouts started ringing through the castle, followed swiftly thereafter by the sounds of battle. Quickly you ran to your room and donned your sword and chainmail vest before dashing out into the hallways to take command of the first band of palace guard that you saw. The battle had progressed to the balcony, and so you led your troops there, ready to fight to defend your home. When you got there, you saw a strange octopus-like creature. Unfortunately, it also saw you.

With inhuman speed, it grabbed you and threw you head over heels over the side of the balcony. You flipped end over end, rushing faster and faster towards the waves - and then, you knew no more.

You don't remember much of the next few days, only fading in and out of consciousness, and some dark THING forcing you to drink something. But when you came to, you were in a strange place. The floor was sand, the walls were stone, but strangest of all, the air was saltwater. You were beneath the sea - and yet somehow, still alive?

Your new surroundings surprised you, but no more than the sight of the beautiful creature that approached you soon after - a \cWitch{\mer} so perfectly formed that it drove all other thoughts out of your mind, including why you looked like \cWitch{\they}. \cWitch{\They} introduces \cWitch{\their}self as \cWitch{} as \cWitch{\they} brought you food and asked you a few questions. And when you were done, \cWitch{\they} kissed you on the cheek, which left you surprisingly lightheaded for hours after.

Living with \cWitch{\them} became your new routine, which in retrospect, you questioned surprisingly little. The questions about your life soon faded to \cWitch{\them} teaching you about strange new abilities that you didn't know you had - the reading of the Tarot - and truly bizzarre questions that you nevertheless did you best to answer. And always at the end, \cWitch{\they} would kiss your cheek, and the lightheadedness would last a little longer each time.

It took you half a year to work up the courage to say no to the kiss, but when you did, you wished you hadn't. At first, \cWitch{\they} just seemed surprised. Then a terrible expression came upon \cWitch{}'s face, and \cWitch{\they} ORDERED you to submit. To your shock, you did. And with a creul smile, she left you, drained and alone.

From that day forward, \cWitch{} dropped all pretenses. You were \cWitch{\their} slave, and she wasn't going to let you forget it. Your training continued, and \cWitch{\their} turned to ripping energy straight from your chest. though you tried to resist \cWitch{\them} at every turn, you continued to obediently follow orders. Unable to escape, and unable to disobey, you lived your days in misery, continuing to struggle against your magical bonds. You were forced to join the Merchant's Guild, and through your hard work and unwilling sacrifice, moved quickly through the ranks. You were \cWitch{}'s cover to rejoining the undersea country of \pAtlantis{}, and another tool in \cWitch{\their} corruption.

Though \cWitch{\they} assured you that the spell was perfectly inescapable, you found that continued resistance actually did weaken the hold that \cWitch{\they} had on you, though this was made much harder by being drained of life force daily. Though you had been forbidden long ago to touch anything in the room around you, you found that by exerting yourself mentally and taking advantage of a loophole in an offhand command you had carefully elicited from \cWitch{\them}, you could look at the books on the shelves of the room around you. After much careful research while you were sure \cWitch{} was asleep, you found the spell - and found how to most effectively go about removing it. You needed a place with a high concentration of magic, and preferably a magician, to deal with the spell. Unfortunately, that didn't fit any place where you could influence \cWitch{} to go normally. But keeping your ears open, you managed to hear about the Neptune Ball at the \pAtlantis{}n Palace, a place teaming with magic. You subtly made sure \cWitch{} knew about it, and began to lay plans ever so painstakingly, to make your escape while there. And so, you bided your time until the day arrived.

Upon reaching the ball, you noticed something interesting. Though \cAriel{} had known you for a year before your dissappearance, \cAriel{\they} didn't recognize you at all! You looked in a mirror, and suddenly understood why - your soul-draining at the hands of \cWitch{} had aged you at least 30 years. You looked nothing like your old self anymore. That meant you couldn't count on \cAriel{\their} help, at least initially.

The other thing was even more unexpected. General \cGeneral{}, your former arms instructor was in attendance! But not only was \cGeneral{\they} a human at the time, \cGeneral{\they} had been lost at sea in the same storm that killed your mother! You need to confirm that your old memories are true, and find out more. Them you must confront \cGeneral{\them} about it, and see what really happened all of those years ago!

Needs an ability that says "`You're old. Be slow."'

\begin{itemz}[Goals]
	\item Break the spell holding you to \cWitch{}!
	\item Acquire the wishing stone - that could be an easy shortcut to removing the spell.
  \item Fulfill the agenda of the merchant's guild as much as is necessary to avoid suspicion.
	\item Find out how \cGeneral{} survived the shipwreck and confront \cGeneral{\them} about it.
	\item Make sure \cWitch{} dies as painfully as possible.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{}
\end{contacts}

\end{document}
