\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cWillow{}}

You are a \cWillow{\prince}, which is awesome, and you get to visit a whole new world, which is even awesomer!

Your life so far has been \emph{the greatest thing ever}. You love your \cAriel{\pa}, \cAriel{}, and your \cEric{\pa}, \cEric{}, and they love you too! You know because they always give you cool toys and tell you all sorts of interesting things about the world! The coolest part is that your \cAriel{\pa} used to be a \emph{\cAriel{\mer}}, and you bet \cAriel{\they} has all \emph{kinds} of cool stories to tell - if only \cAriel{\they}'d let you in on the secrets!

Of course, your \cAriel{\pa} isn't \emph{that} cool. \cAriel{\They} tried to keep you from finding out about merfolk, and even banned you from playing in the ocean. Your parents can be so weird some times. They wouldn't even tell you why. But it didn't really matter because it is not like you listened to them anyway. You regularly snuck out of the palace and went down to the ocean to play, imagining you could breath under water, or turn into a fish.

It turned out to be a good idea too, because one day, you came across your \cAriel{\pa} at the shore, talking with a \cKing{\human} half submerged in the water. You thought it was weird, so you you hid behind a rock, and watched. You were so surprised when the \cKing{\human} turned out not to be a \cKing{\human} at all. \cKing{\They} lifted \cKing{\them}selves out of the water, and you saw that \cKing{\they} had the tail of a fish instead of legs! You ran out to look, and found it was true -- \cKing{\they} was a \cKing{\mer}!! Your wildest dreams were true! 

When your \cAriel{\pa} told you to go back to the palace and forget about the enchanted undersea world of merfolk, you understandably started to throw a tantrum. How could \cAriel{\they} tell you to just forget the biggest thing that had ever happen to you? You were really just getting started when the \cKing{\mer} admonished you to act like a \cWillow{\prince}. Apparently this \cKing{\mer} was actually your grand\cKing{\parent}! (That meant that \cAriel{\pa} had once been a \cAriel{\mer} too! Awesome!) \cKing{\They} promised that if you behaved, you could attend a ball in \pAtlantis{}!

Obviously there are a \emph{bazillion} things you need to know about ``\pAtlantis{}'' and everywhere else under the sea, but even you know there are limits to what you can find out in one go. So, like the logical \cWillow{\prince} and future ruler that you are, you made sure to decide on a few priorities for yourself before the start of the ball.

First, make friends! Any budding \cWillow{\prince} knows that making friends means power, so you want to make as many friends as possible. They're all going to be in one place and not going anywhere, so now would be a great time! You also wanna get to know your grand\cKing{\pa}, who your \cAriel{\pa} talks about a lot now that you know. \cKing{\They} sounds really nice, and maybe \cKing{\they}'ll give you presents!

Second, your \cAriel{\pa} wouldn't tell you many stories about the world under the water, but \cAriel{\they} did tell you about the dancing. You were immediately enchanted by the idea of dancing \emph{in 3D}, so while you're here, you want to learn as much about that as possible!

Third, as you were walking in here, you heard a crazy old man yelling something about a \iWishingStone{\MYname}. You don't know what that is, but it sounds super neat, so you really want to find it!

This all sounds like quite a lot of stuff to do in just four hours at the ball! Of course, if you could find some way to become a \cWillow{\mer}, then you'd have all of the time in the world. Plus you'd get to move in 3D \emph{all the time}. Maybe you should work on that first, because that sounds kind of awesome...

\begin{itemz}[Goals]
  \item Find some way to become a \cWillow{\mer} without letting your \cAriel{\parent} find out!
  \item Learn as many dance styles as possible.
  \item Make as many friends as possible, especially with your grand\cKing{\pa}.
	\item Find the \iWishingStone{\MYname}!
  \item Find out everything else too. If you learn anything cool, go tell your \cAriel{\parent}.
	\item Figure out why you feel funny. It might be because you're breathing water right now, but that doesn't feel \emph{quite} right...
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cAriel{}} Your \cAriel{\parent}. She's here to protect you and hang out with her family.
	\contact{\cKing{}} Your grand\cKing{\parent}. He is trying to get a treaty or something signed. It sounds kinda important -- but clearly not as important as spending time with you!
\end{contacts}

\end{document}
