%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nGazaStrip{}}

\begin{page}{first}

Your family has recently discovered a great wealth of pearl bearing clams in the \pGazaStrip{}. It is unfortunate that the land is under dispute in the treaty discussions tonight. It is part of why you agreed to attend the \cExExKing{} Ball. You intend to secure this land for \pAtlantis{}. Your family will have no trouble monopolizing the land once it is secure. 

To accomplish this, you will have to figure out why the \pPacifica{}n's care so damn much about the land -- surely they don't know about the pearls? Go and make at least 2 \pPacifica{}ns tell you why the \pGazaStrip{} is so important to them. Once you do so, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

The only thing worse than fighting someone who is in it for the money, is fighting someone who is in it for moral reasons. They never know when to quit. Unfortunately, it looks like the \pPacifica{}ns are after the \pGazaStrip{} for moral reasons. Their precious Kraken was supposedly sighted there, not so long ago.

You will need to contact your family and make sure that they are up for this fight. You may have to burn a lot of political capital and take some major risks to pull this off. Write a note to your family (clearly mark the note as an ``in game'' item) and deliver it to the nearest page (NPC) who will deliver it to your family. In 20 minutes, you may go inquire with a page as to the response. Once you have \iCipherLetter{}, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Your family has of course written to you in code, just in case the letter was intercepted. The letter indicates that the land is of great importance to your family, and they are more than willing to take the risks involved with securing the land. 

Well, if they are determined, then you'd better set things in motion. First thing's first, talk to \cPlant{} and convince him to make a formal (written) declaration that the Explorer's Guild will veto any treaty that does not secure the \pGazaStrip{} for \pAtlantis{}. If \cPlant{\they} is currently indisposed, or refuses to cooperate, you may forge such a document by writing your request down (and clearly marking it as an ``in game'' item), and giving it to a page, who will deliver it to some contacts of yours outside the palace. Once you have the real or forged document in hand, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Now to convince the \cKing{\King}. Present the document to \cKing{\King} \cKing{}. Make it very clear to \cKing{\them} that the Explorer's Guild is a crucial part of these negotiations and that \cKing{\they} cannot afford to ignore your demands. Use this fact throughout the evening to delay the treaty if you haven't completed your research. Once you have presented the document to \cKing{}, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Now for the real digging. Go through the papers in the \sEmbassy{}, and find out more specifics about this giant squid sighting. Once you have find a date for the sighting, and the person who sighted it, turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Okay, you have a date (\cKraken{\MYname}). Now to prove that the Kraken was elsewhere. Legend has it that the Kraken causes shipwrecks on a regular basis. Well, if anyone would know, it would be the Explorer's Guild. Go and check their files and journals. (You may take the item from ``\sJournals{}'' in the Explorer's Guild.)  turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

The music box isn't there! What is going on? Surely the music wouldn't lead you falsely. As you stare in despair at the small crevice where the box so neatly would have fit, you realize that a faint green light flashes occasionally. Is it a clue? It must be!  Search for 3 green stickers throughout game space. The numbers on the signs with green stickers will lead you to the music box. Once you find the new room, search the room for ``\sPacketB{}''. If the music box is there, turn to page \nbref{eleventh}, if it is not there, turn to page \nbref{eight}.

\end{page}

\begin{page}{eighth}

Gone. Or maybe never there? You must be getting closer though. You must be. Okay, deep breath. Maybe the music is just too faint to hear right now. You'll need to build something to amplify the sound. Find an \iConch{}, a <insert item> and a <insert item>. Put them next to each other in alphabetical order by name to build the amplifying device. The second digit of each item number will lead you to the room where the music box is. Go to that room and search for ``\sPacketC{}''. If the music box is there, turn to page \nbref{eleventh}, if it is not there, turn to page \nbref{ninth}.

\end{page}

\begin{page}{ninth}

Okay, someone is clearly moving the music box. Who would do such a thing? Never mind, it just makes it all the more imperative that you find it. Get a magician to cast a ``perceive magic'' spell on location C. You must tell them what you are looking for in order for them to help you. Once they have done so, turn to page \nbref{tenth}.

\end{page}

\begin{page}{tenth}

You follow a pulsing trail of light that no one else can see to $<$insert room$>$. Search for ``\sPacketD{}''. Once you find it, take the music box out and turn to page \nbref{eleventh}.

\end{page}

\begin{page}{eleventh}

You've found it! The music box! All you have to do now is put it back on display and wind it up. Go to the sign for the empty pedestal where the music box should sit, and swap it for the sign underneath. Put the music box in the envelope attached to this sign Then spend 2 minutes winding the music box with your key. You must have the key to do this action. Once you have done so, you may turn to page \nbref{twelfth}.

\end{page}

\begin{page}{twelfth}

It's done. With the music box wound, \pAtlantis{} will be safe for another decade. If you haven't done so already, you should find one of your daughters and pass the secret of the music box on to them.

\end{page}

\endnotebook

\end{document}
