\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bAtlantian{}}

As a citizen of \pAtlantis{}, you are well familiar with your country's recent history and economic structure.

{\bf History:}\\
King \cKing{\MYname{}} is the current ruler of \pAtlantis{}. \cKing{\They} has ruled for almost 35 years and it is generally accepted that \cKing{\they} is a good and benevolent king despite the terrible misfortunes that have defined his rule.

His reign began in blood, when his father, King \cExKing{\MYname{}}, and most of his family, were killed by \pPacifica{}n assassins. \cKing{\MYname{}} took up his father's \iTriton{\MYname{}}, and rallied the kingdom to repel the ensuing invasion. For much of King \cKing{\MYname{}}'s reign, \pAtlantis{} has been in open war with \pPacifica{}. Repeated skirmishes and battles as well as maintaining constant vigilance along the border has cost \pAtlantis{} dearly both in money and in lives. Recently however, King \cKing{\MYname{}} has opened negotiation talks with the \pPacifica{}ns, and has even invited a delegation of \pPacifica{}ns to attend this year's \cExExKing{} Ball. Many merfolk see this as a sign that this war might finally be drawing to a close

King \cKing{\MYname{}} took a wife soon after assuming the throne. \cQueen{\King} \cQueen{\MYname{}} was beautiful and gracious, even if she bore little physical resemblance to her Caribbean kin, being olive skinned and dark haired. They had 2 beautiful daughters, one of whom is gracious, poised, and committed to Atlantis. The other one was named \cAriel{\MYname{}}. \cAriel{\MYname{}} was always getting into trouble, and always asking about the human world above. 

21 years ago, Queen \cQueen{\MYname{}} disappeared without a trace. Rumors flew that it was the work of the Sea Witch, \cWitch{\MYname{}}, but nothing was ever proven.  This loss of \cKing{\their} \cQueen{\spouse{}} shook \cKing{}, and he emptied much of \pAtlantis{}'s depleted coffers in a fruitless search for her.

Disturbed by \cAriel{\them} father's preoccupation, \cAriel{} eventually went to live on the surface, and married a human prince. The whole affair was hushed up by the royal family, so little is known about how \cAriel{\they{}} managed it. But, since \cKing{} dissolved the \pMagician{} almost immediately after, rumor has it that \cAriel{\they} used magic to become human. The loss of \cAriel{} seemed to finally break King \cKing{\MYname{}}. In the years since, \cKing{\they{}} has become reclusive, erratic, and whispers are surfacing that \cKing{\they{}} may no longer be fit to be \cKing{\King}.

It has been 14 years since \cAriel{\MYname{}} forsook Atlantis, but \cAriel{\they{}} and \cAriel{\their{}} \cEric{\spouse{}} are scheduled to attend this year's ball. There is great speculation as to why.

Life goes on in Atlantis. Things are peaceful, except along the border, trade is good, and everyone looks forward to the annual \cExExKing{} Ball. While the King's private bash is extremely exclusive, all over Atlantis, parties are thrown to celebrate the turning of the year.\\

{\bf Guilds:}\\
The economy and government of \pAtlantis{} centers around the guilds. As far back as anyone can remember, \pAtlantis{} has had five guilds that provide a division of tasks to help \pAtlantis{} run smoothly. They each elect 1 official for a 2 year term that make up a council that advises the King.  Members of the royal family may belong to guilds but may not be elected to the council (they are not barred from holding high ranks in the Guilds, and the representative to the council is not necessarily the most powerful Guild Member). The guilds are:
\begin{itemize}
  \item {\bf Explorer's Guild:} Composed of explorers, cartographers, archeologists, historians, librarians etc. They handle the acquiring and storing of data (of all kinds) for \pAtlantis{}.
  \item{\bf Merchant's Guild:} Composed of traders, economists etc. They claim that despite the recent lull in the war, \pAtlantis{} is  still on the brink of economic collapse. Most people dismiss them as being overly pessimistic.
  \item {\bf Artisan's Guild:} Composed of the craftsmen of Atlantis. They are often at odds with the Merchant's Guild over which guild has jurisdiction over the nations natural resources.
  \item {\bf Guardian's Guild:} In charge of the military of \pAtlantis{} and security for all the nobles. Their most prestigious role is to guard the royal family.
  \item {\bf Magician's Guild:}  Now formally dissolved. Used to be a voice for \pAtlatis{}'s magicians to ensure that magic was being employed for \pAtlantis{}'s best interest and not being exploited.
\end{itemize}

\end{document}