\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bGMPotions{}}

{\bf Spells and Potions:}
The spells and potions a magician can use are based on their level. Spells are represented as ability cards. All potions follow a standard brewing strategy (see below the list). Potions have distinctive colors and can be recognized by magicians by their color. 

Here are the known spells and potions that may be useful this evening:
\begin{enumerate}
  \item Level 1
   \begin{enumerate}
     \item Healing Potion (RED) - 15 minutes to make. Can cure wounds (the target will wake up, fully healed after 10 seconds) and heal most poisons. 
     \item Lesser Dispel - Instant spell. Can completely remove a magical effect of level-2 or lower. Can be used on magical locks to reduce the necessary decking hand by one (decking hand requirement cannot be reduced below 1). Can disrupt shape shifters.
   \end{enumerate}
  \item Level 2
   \begin{enumerate}
     \item \aPerceive{} - Instant spell. Can be used to determine someone's $\alpha$ score and detect magical effects.
   \end{enumerate}
  \item Level 3
     \begin{enumerate}
     \item Latent Poison (GREEN) - 30 minutes to make. This poison can be cured with a healing potion or \aFirstAid{}. In order to administer the poison, the magician must successfully attach a sticker to the target without the target noticing. The magician must then go and inform a GM. The GM will handle the rest. GMS: write ``Open in 20 minutes''.
   \end{enumerate}
   \item Level 4 - No useful spells or potions
   \item Level 5
    \begin{enumerate}
     \item Transformation Potion (ORANGE) - 20 minutes to make. This potion will transform a merperson into a human or vice versa. This transformation reduces your CR by one (your CR cannot go below zero). If a player returns to the form they started the game in, it negates the CR reduction.
   \end{enumerate}
   \item Level 6
    \begin{enumerate}
      \item \aGreaterDispel{} - Instant spell. Can break spells up to level-4. Can be used on magical locks to reduce the necessary decking hand by two (decking hand requirement cannot be reduced below 1). Can disrupt shape shifters.
    \end{enumerate}
   \item Level 7
    \begin{enumerate}
      \item Deadly Poison (BLACK) - 90 minutes to brew. This poison {\bf cannot} be cured with a healing potion or \aFirstAid{}. In order to administer the poison, the magician must successfully attach a sticker to the target without the target noticing. The magician must then go and inform a GM. The GM will handle the rest. 
    \end{enumerate}
\end{enumerate}


\end{document}