\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bMerchant{}}

As a member of the Merchant’s Guild, you are charged with safeguarding the economy of \pAtlantis{} and representing the common worker.

{\bf History}\\
The Merchant’s Guild protects the economic interests of \pAtlantis{}, and represents traders, economists and many other sectors of the \pAtlantis{}n economy. The Guild is in near constant conflict with the Artisan’s Guild over the exact jurisdiction of the two guilds. The guilds in fact used to be one guild, but a number of artisan’s broke off and formed a new guild, claiming that the Merchant’s guild was too caught up in the politics and was failing to represent the common worker. This is an accusation that the Merchant’s Guild vehemently denies.

In the recent negotiations with \pPacifica{}, the Merchant’s Guild has played a very prominent role. The guild has many demands and a large stake in the treaty. In fact, all of \pAtlantis{} has a larger stake than they know. Economists predict that \pAtlantis{}’s economy will collapse within a decade if the war expenditures aren’t curbed.

{\bf High Ranking Officials}\\
Head of the Guild: Nautilus -- Nautilus is away on unexpected, urgent personal business and could not attend tonight’s ball.\\
Representative to the Council of Advisors: \cSlave{}

{\bf The Treaty}\\
As a member of the Merchant’s Guild, you are interested in having the treaty accomplish several things. 

Primarily, you would like to see peace between your two nations. The war has been a constant drain on the nation’s coffers, and the fear in the populace has damaged the economy. Peace would also offer many new trade opportunities, which would be the only way to reverse the damage inflicted by such a prolonged war. {\bf In the absence of new information, if the treaty doesn’t include peace with \pPacifica{}, then you should highly consider vetoing the treaty.}

The Guild is also looking to receive reparations for the \pPacifica{}ns aggression and the economic damage \pAtlantis{} has sustained. The Guild would further like open borders, as this would foster trade and begin to repair the massive damage the war has done to the economy.

\end{document}