\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bPacifican{}}

You are a citizen of \pPacifica{}, and therefore know much about the history of \pPacifica{}, but little about the strange realm of \pAtlantis{} where you now find yourself.

{\bf History of the War:}
The war with \pAtlantis{} began several generations ago. No one remembers why \pAtlantis{} attacked on that fateful day, but the aftermath is well remembered. Thousands of \pPacifica{}ns have died in the war. While the balance of power has tipped back and forth over the decades, the two kingdoms seem fairly evenly matched. Recently however, \pPacifica{} has consolidated its forces for an inevitable, crushing counterattack while suffering minimal losses. It is from this position of power that \cPacificanRuler{\King} \cPacificanRuler{} has chosen to parlay with the \pAtlantis{}n royal family.

King \cKing{\MYname{}} has sought negotiations since a decade ago, but negotiations have always been rocky. Several cease fires have been issued and broken, and despite every effort, no treaty has materialized. Though hopes for this treaty are similarly slim, \cKing{\King} \cKing{} has invited a delegation of \pPacifica{}ns to attend this year's \cExExKing{} Ball to sign the treaty that has been half a year in the making.\\

\pIndia{} has remained neutral throughout the long war.

{\bf The Royal Family:}
\cPacificanRuler{\King} \cPacificanRuler{} is a wise and just ruler. The \cPacificanRuler{\King} always listens to the will of the people and advocates for their interests, and so is much beloved in \pPacifica{}. \cPacificanRuler{\They} is not without fault, though, as \cPacificanRuler{\they} can often be covetous of wealth and wrathful in the face of insult. In one of \cPacificanRuler{\their} worse moods, the \cPacificanRuler{\King} demanded a token of respect be retrieved from \pAtlantis{} by the visiting delegation. Anyone who has worked directly with the \cPacificanRuler{\King} knows that painful punishment awaits those that do not fulfill \cPacificanRuler{\their} whims.

The former \cPacificanRulerSpouse{\King} \cPacificanRulerSpouse{} was also beloved by the people, but was unfortunately a bit too hands on with \cPacificanRulerSpouse{\their} forays into the enemy field, and was killed years ago. In \cPacificanRulerSpouse{\their} place, \cPrince{\Prince} \cPrince{} has stepped up to fill \cPrince{\their} \cPacificanRulerSpouse{\parent}'s role. \cPrince{} commands border patrols and leads small skirmishes regularly, as well as acts as a general in more major battles. \cPrince{} is also quickly becoming an accomplished diplomat, and as such has been entrusted with the delicate Neptune Ball political situation. \cPrince{\they} is much beloved by \cPrince{\their} \cPacificanRuler{\parent}, \cPacificanRuler{\King} \cPacificanRuler{}, though \cPacificanRuler{\they} can be just as harsh on \cPrince{} as any of \cPacificanRuler{\their} other subjects.\\

{\bf Current Life in \pPacifica{}:}
While far from peaceful, life in \pPacifica{} is at least free and governed fairly. The war is thought of as a necessary evil, one which the people strive to take their minds off of with many festivals and religious ceremonies. Waltz is a popular pastime, and is partaken of by commoners and nobles alike.\\

\begin{itemize}
  \item {\bf Religion:} \pPacifica{}ns worship the power of the squid, who are the incarnations of ancient Gods upon this land. Primary among these is the Kraken, whose crushing power represents the most ancient of Gods, and whose very passage consecrates the waters through which it passed. The humans, who hunt the squid, are your mortal foes for this very reason. The \pGazaStrip{} is important to you because that is the last place that the Kraken was sighted, and is, as such, the holiest of holy grounds.
  \item {\bf \cPolio{}:} \cPolio{} is the disease that threatens the very existence of \pPacifica{}. The symptoms are flu-like at first, but quickly escalate into life-threatening territory. Even worse, if you survive the worst of it, you are permanently crippled, forever short of breath and skin mottled by boils. It also reduces fertility, a condition that can be easily passed to your children. The disease has reached epidemic proportions, especially among the poor, and shows no sign of stopping. 
  \item {\bf The Black Market:} It is well known in Pacifica that there is a merchild smuggling ring of great influence. The ring smuggles children into and out of \pPacifica{}, selling them to the families that can no longer concieve, either because of \cPolio{} or for other reasons. \cPacificanRuler{\King} \cPacificanRuler{} nominally opposes such criminal activity, but as their main focus is on stealing merchildren from outside of \pPacifica{}, efforts to stamp them out have been half-hearted at best.
  \item {\bf The Assassin's Guild:} The Assassin's Guild is an extremely influential force in \pPacifica{}. In generations past, the Assassin's Guild openly sold the skills of assassins, but in recent years, have cleaned up their act, and pursue only legitimate means in a purely open manner. The \cPacificanRuler{\King} has publicly pardoned the organization after an extensive audit, and has welcomed them back into the larger political discourse.
  \item {\bf Magic:} Magic is free and celebrated in \pPacifica{}, and is often employed to improve the lives of its citizens. Magicians are often employed to supplement the armed forces and protect important targets.
\end{itemize}

{\bf Goals:} Find an item marked "`valuable"' to bring back for your \cPacificanRuler{\King}.

\end{document}