\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bAtlantian{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

{\bf History of the War:}\\
The war with \pPacifica{} began several generations ago. No one remembers why \pPacifica{} attacked on that fateful day, but the aftermath is well remembered. Thousands of \pAtlantis{}ns have died in the war. While the balance of power has tipped back and forth over the decades, the two kingdoms seem fairly evenly matched. Recently however, \pAtlantis{} has won a small string of strategic victories. From this position of power, \cKing{\King} \cKing{} has chosen to extend the olive branch to \pPacifica{}.\\

King \cKing{\MYname{}} opened negotiation talks with the \pPacifica{}ns nine years ago. Negotiations have been rocky. Several cease fires have been issued and broken, and despite every effort, no treaty materialized in eight years of negotiations. In the past two years or so, \cPrincess{\Prince} \cPrincess{} has joined \cPrincess{\their} \cKing{\parent} in negotiations. It seems that progress is finally being made. \cKing{\King} \cKing{} has  invited a delegation of \pPacifica{}ns to attend this year's \cExExKing{} Ball to sign the treaty that has been half a year in the making.\\

{\bf History of the Royal Family:}\\
King \cKing{\MYname{}} is the current ruler of \pAtlantis{}. \cKing{\They} has ruled for almost 35 years and it is generally accepted that \cKing{\they} is a good and benevolent king despite the terrible misfortunes that have defined his rule.

His reign began in blood, when his father, King \cExKing{}, and his entire family except \cKing{\their} little \cPlant{\sibling}, \cPlant{}, were killed by \pPacifica{}n assassins. It is still a mystery how the strike force got into the palace. \cKing{} took up \iTrident{\MYname{}}, and rallied the kingdom to repel the ensuing invasion.

\cKing{\King} \cKing{} took a \cQueen{\spouse} soon after assuming the throne. \cQueen{\King} \cQueen{} was beautiful, gracious, and well loved by the people. They had 2 beautiful children. \cPrincess{\Prince} \cPrincess{}, the younger \cPrincess{\offspring}, has recently blossomed into a persuasive diplomat. The older \cAriel{\Prince} was named \cAriel{}; \cAriel{} spent almost all of \cAriel{\their} time with the Explorer's Guild and often neglected \cAriel{\their} royal duties. 

However, all is not well in \pAtlantis{}'s royal family. \cPlant{\Prince} \cPlant{} has become paranoid and delusional as the years have gone by. \cPlant{\They} publicly and loudly claims all kinds of conspiracies are afoot. Twenty one years ago, \cQueen{\King} \cQueen{} was kidnapped and killed by \pPacifica{}n assassins. \cAriel{\Prince} \cAriel{} ran away from \cAriel{\their} royal duties and married a human prince. The whole affair was hushed up by the royal family, so little is known about how \cAriel{\they{}} managed it. But, since \cKing{} dissolved the \pMagician{} almost immediately after, rumor has it that \cAriel{\they} used magic to become human. The loss of most of the family \cKing{\they} had tried to rebuild seemed to finally break \cKing{\King} \cKing{}. In the years since, \cKing{\they{}} has become reclusive, erratic, and whispers are surfacing that \cKing{\they{}} may no longer be fit to be \cKing{\King}.\\

{\bf Religion:}\\
Most \pAtlantis{}ns subscribe to the Church of the Tides. The church worships the moon for it's power to control the tides. The church preaches love, forgiveness, and the salvation of the weak. It is believed that your soul will be reincarnated again and again until you live a life pure enough to earn you a place among the stars. The care of your eternal soul is particularly important, because there are spirits that dwell in the center of the earth, who if given the opportunity, would imprison your soul for eternity.

The Church of the Tides believes that some individuals are cursed by the moon to be shape shifters, forever without a true form or identity. Shape shifters are unable to control their transformations, and when they do transform, are a menace to everyone. The priests of the church have therefore taken it upon themselves to protect the citizens of \pAtlantis{} from shape shifters, hunting them down wherever they appear to terrorize an innocent community.\\

{\bf Guilds:}\\
The economy and government of \pAtlantis{} center around the guilds. As far back as anyone can remember, \pAtlantis{} has had five guilds that provide a division of tasks to help \pAtlantis{} run smoothly. They each elect 1 official for a 2 year term that make up a council that advises the King.  Members of the royal family may belong to guilds but may not be elected to the council (they are not barred from holding high ranks in the Guilds, and the representative to the council is not necessarily the most powerful Guild Member). The guilds are:
\begin{itemize}
  \item {\bf Explorer's Guild:} Composed of explorers, cartographers, archeologists, historians, librarians etc. They handle the acquiring and storing of data (of all kinds) for \pAtlantis{}.
  \item{\bf Merchant's Guild:} Composed of traders, economists etc. They claim that despite the recent lull in the war, \pAtlantis{} is  still on the brink of economic collapse. Most people dismiss them as being overly pessimistic.
  \item {\bf Artisan's Guild:} Composed of the craftsmen of Atlantis. They are often at odds with the Merchant's Guild over which guild has jurisdiction over the nations natural resources. They have declined to attend this year's ball in protest of the prominent role that \cKing{\King} \cKing{} has allowed the Merchant's Guild to play in negotiations.
  \item {\bf Guardian's Guild:} In charge of the military of \pAtlantis{}. Their most prestigious role is to guard the royal family.
  \item {\bf Magician's Guild:}  Now formally dissolved. Used to be a voice for \pAtlantis{}'s magicians to ensure that magic was being employed for \pAtlantis{}'s best interest and not being exploited. \cManta{} is the only magician still allowed to practice, and only under very strict regulation from the royal family. There are unconfirmed rumors that powerful, criminal magicians like \cWitch{} are still practicing magic in the deepest caverns of \pAtlantis{}.\\
\end{itemize}

{\bf The \cExExKing{} Ball:}
The attendee list for the \cKing{\King}'s private party includes:
\begin{itemize}
  \item The \pAmerica{} representative, \cAriel{\King} \cAriel{}. It has been 14 years since \cAriel{\MYname{}} forsook Atlantis, so there is great speculation as to why \cAriel{\they} has chosen to attend this year.
  \item The \pPacifica{}n representative, \cPrince{\Prince} \cPrince{} and a small delegation of diplomats.
  \item The Explorer's Guild representative, \cPriest{}.
  \item The Merchant's Guild representative, \cSlave{}.
  \item The Guardian's Guild representative, General \cGeneral{}.
\end{itemize}


\end{document}