\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bGuardian{}}

As a member of the Guardian’s Guild, you are charged with the protection of \pAtlantis{} and all of its citizens.

{\bf History}\\
The Guardian’s Guild has a rich and noble history. The guild has been the protector of \pAtlantis{} as far back as the records go. What began with a loose alliance of town militias has grown into one of the best organized and farthest reaching militaries under or above the ocean.

The Guild trains bodyguards for high ranking officials as well as managing the day to day of the war. Generals consult with \cKing{\King} \cKing{} and launch assaults against \pPacifica{}, and so far, \pAtlantis{} is winning the war, although at a terrible cost.

{\bf High Ranking Officials}\\
Head of the Guild: Kratos\\
Representative to the Council of Advisors: General \cGeneral{}

{\bf The Treaty}\\
As a member of the Guardian’s Guild, you are interested in having the treaty accomplish several things. 

The two most important things to the Guardian’s Guild are the issues of the prisoners of war and the military alliance against an alleged Indian threat. Several important \pAtlantis{}n officials have been captured, including the head of the Guardian's Guild, Kratos, and the continued success of the Guild's military ventures depends in significant part to their safe return. The alliance against the supposed Indian aggression is unnecessary and superfluous - the reports of Indian aggression have yet to be substantiated.  The Guild does not trust \pPacifica{}. Without proof of their trustworthiness, you cannot in good conscience agree to more than a ceasefire. {\bf In the absence of new information, if the treaty includes a military alliance between \pAtlantis{} and \pPacifica{}, or doesn’t involve the exchange of POWs, then you should highly consider vetoing the treaty.}

The Guild is also against open borders. There’s no discernible benefit to \pAtlantis{}, and the additional security required would require time and funding that the Guardian’s Guild doesn’t currently have.

\end{document}