\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bMagician{}}

As a member of the Magician's Guild, you are part of a powerful cabal of magicians. The guild spans \pAtlantis{} and \pPacifica{},and has a long and storied history.

{\bf History:}\\
The Magician's Guild began in \pAtlantis{} 300 years ago. At that time, \pAtlantis{} and \pPacifica{} were friendly with each other, and so the guild soon expanded to incorporate magicians in both oceans. Information and spells flowed freely between the branches of the guild, and both countries profited from the exchange. For many years, the Magician's Guild worked closely with the Church of the Tides to hunt down shape shifters since some spells can be used to disrupt a shape shifter's transformation.

When relations between the countries soured, the Magician's Guild kept up friendly contact for some time, although the exchange of information was somewhat more limited. When \cKing{\King} \cKing{} disbanded the Magician's Guild in \pAtlantis{}, the \pAtlantis{}n magicians either went to ground or fled to \pPacifica{}. Only \cManta{}, the \cKing{\King}'s trusted advisor, was allowed to continue practicing, and only under strict supervision. While some claimed that \cManta{} abandoned \cManta{\their} fellow magician, these accusations were soon laid to rest when \cManta{} secretly revived the Magician's Guild a few years ago. The guild has operated in the shadows ever since.

\cManta{} is currently the head of the Magician's Guild in \pAtlantis{}.

{\bf Secrecy:}\\
Since it is illegal to practice magic in \pAtlantis{}, it is imperative that all members of the Magician's Guild practice the utmost secrecy. Magicians are put to death in \pAtlantis{}, and any breach in confidentiality risks exposing the entire \pAtlantis{}n branch.

{\bf Betrayal:}\\
If any member of the guild suspects another member of betraying the ideals, mission or secrecy of the guild, they can submit a formal accusation. An independent investigation will be conducted by the guild over the next few weeks, and the judicial review board will make final ruling within a month. During the investigation, the accused is considered to be on probation, and will have restricted access to guild resources. \emph{(No in game effect.)}

{\bf Induction:}\\
Two current members of the Magician's Guild may induct a promising candidate through the Guild's ancient rites of induction. Eligible candidates will have an $\alpha$ score of 1. Magicians of level 2 and higher have a ``\aPerceive{}'' ability which allows them to determine the $\alpha$ score of a person.
\begin{description}
\item[First] Find the guild crest - it has been removed from the main guild hall, but is likely still somewhere in the castle. 
\item[Second] Both inducting members must spend 1 minute together laying down an ancient magical symbol around the feet of the inductee in \iChalk{} on the ground in front of the crest. You should explain the workings of the rune to the inductee for future inductions. The magical symbol resembles a six pointed star. 
\item[Third] All three participants should observe a moment of silence for one minute as the magical energy filters through the inductee and the magical symbol. \item[Fourth] one of the current members should swear in the inductee with a call and response swearing them to secrecy and to uphold the ideals and traditions of the guild. You will need to read the oath out of the \iBook{}m which is actually a secret magical tome (though you'll actually be making up the oath). 
\item[Fifth] Take the bluesheet from under the guild crest and give it to the new inductee - they are now an active member.
\end{description}

The new member is inducted as a level-1 magician.

{\bf Spells and Potions:}
The spells and potions a magician can use are based on their level. Spells are represented as ability cards and are used as instant abilities. All potions follow a standard brewing strategy (see below the list). Potions have distinctive colors and can be recognized by magicians by their color (Lay people don't know what color the different potions are). Potions are represented as consumables that can be obtained at the cauldrons where they are brewed.

Potions can be administered in 2 ways. A willing or helpless target can drink the potion, in which case, the person administering the potion should hand over the potion consumable to the target. An ignorant target can also be injected with a potion. The person administering the potion must successfully stick a sticker on the target without being caught in the act by the target or anyone else. (Stickers can be acquired at the cauldrons.) The person who is attempting to administer a potion should then find a GM, explain who the potion is targeting, and hand over the potion. The GM will handle the rest.

{\bf Current Members:}
\begin{itemize}
\item \cManta{} - Head of the \pAtlantis{}n branch of the guild.
\item \cWitch{\MYname} - A powerful \pAtlantis{}n magician.
\item \cBodyguard{} - A high ranking member of the \pPacifica{}n branch of the guild.
\end{itemize}




\end{document}