\documentclass[blue]{NeptuneBall}
\begin{document}
\name{\bPacifican{}}

You are a citizen of \pPacifica{}, and therefore know much about the history of \pPacifica{}, but little about the strange realm of \pAtlantis{} where you now find yourself.

\pPacifica{} is a proud nation. Once it was a prosperous nation too. But almost 100 years ago, the tyrant \cExExKing{\MYname{}} launched a surprise attack on \pPacifica{}, carving a wide swatch of destruction that left the capital in ruins. To add insult to injury, \cExExKing{} kidnapped \cMother{\Prince} \cMother{\MYname{}} and took \cMother{\them} as a prisoner of war. It was only the quick action of \cMother{\them} brothers that allowed her to be recovered. Even so, she was already with child from \cExExKing{}. It is fortunate for the little bastard's sake that he did not survive childbirth. \cMother{}, once the most beautiful and precious gem of \pPacifica{}, was cloistered in a castle far to the north, and died quietly 15 years later.

Immediately after the \pAtlantis{}n invasion, several powerful political factions sought to steal the throne from the current Queen, and the country devolved into a bunch of waring feudal states. Almost three decades of war took it's toll on the people, and when a charismatic young mer\cPacificanRuler{\human{}} surfaced in the country and began talking about reunification, people listened. It certainly didn't hurt that he was the hero of the Angola Plain Operation from 15 years earlier. \cPacificanRuler{\MYname{}} consolidated power at an alarming rate, and soon had the backing of nearly half of Pacifica.

\cPacificanRuler{\They{}} concocted a scheme to steal the \iTriton{\MYname{}}, \cKing{}'s center of power, and take revenge on Atlantis. When the thieves failed to retrieve the \iTriton{\MYname{}}, King \cKing{\MYname{}} tore through huge swatches of Pacifica, leaving the barest shambles where the merpeople were still struggling to rebuild from the civil war. \cPacificanRuler{\MYname{}} used this travesty to bring the rest of \pPacifica{} under \cPacificanRuler{\their{}} strict control. \cPacificanRuler{} also quickly delivered another major victory, this time in the Caribbean, cementing his control of the country. Under \cPacificanRuler{\MYname{}}'s military rule, Pacifica rebuilt. The country was no longer a cultural rival to Atlantis, but it was a quickly becoming the superior military power. \cPacificanRuler{}  held absolute power for 25 years.

Not everyone was thrilled with the military rule however, and a growing movement started to call for peace with Atlantis about a decade ago. Surprisingly, \cPacificanRuler{\MYname{}} seemed to look with favor on this idea, and when a request to open diplomatic talks arrived from Atlantis some eight years ago, \cPacificanRuler{\they{}} quickly appointed a team. Now, an invitation to the \cExKing{\MYname{}} Ball is a strong omen of success. Tonight a treaty will be signed that will usher in an era of peace that will ease \cPacificanRuler{\MYname{}}'s strangle-hold on the country.

\end{document}