\documentclass[white]{NeptuneBall}
\begin{document}
\name{\wInheritance{}}

\emph{This is a copy of the official ``Line of Succession'' document, available in \sMuseum{}. (This is an in game, transferable item)}

To determine who is next in line of succession, follow the list below until you find the first eligible candidate. Assume all classifications that could have multiple members (more than one male child for example, process in order of age). Women who marry into another line of succession forfeit their position in line for the throne of their old kingdom. Bastards of proven lineage are eligible. For example, a bastard cousin is considered in the line of succession as appropriate.

From the last \emph{confirmed} (not acting) ruler of \pAtlantis{} power passes to:

\begin{enumerate}
\item Male children
\item Female children
\item Husband or Wife
\item Brothers 
\item Sisters
\item Brothers-in-law
\item Sisters-in-law
\item The Father
\item The mother
\item Uncles on the {\bf father’s} side
\item Uncles on the {\bf mother’s} side
\item Aunts on the {\bf father’s} side
\item Aunts on the {\bf mother’s} side
\item Male cousins on the {\bf father’s} side
\item Male cousins on the {\bf mother’s}side
\item Female cousins on the {\bf father’s} side
\item Female cousins on the {\bf mother’s} side
\end{enumerate}

If for some reason, no eligible candidate can be  found, the Council of Advisors will elect a new monarch in a closed meeting as soon as possible. (out of the scope of the game)

If power passes to a new person, the acting monarch is considered only a steward until confirmed. If the discredited person manages to reestablish their eligibility before the acting monarch is confirmed they can re-assume power immediately. The process of actually confirming the monarch takes about a week and is the duty of the Council of Advisors.

In order to pass power to the acting monarch:
\begin{enumerate}
\item The eligibility of the candidate must be verified by at least 2 \pAtlantis{}n (using the chart above).
\item They need to take an oath to protect Atlantica in front of 3 witnesses (at least 1 must be \pAtlantis{}n).
\end{enumerate}

\iTrident{} rightfully belongs to the acting ruler of \pAtlantis{}. The acting monarch should not hesitate to use his or her extensive authority to acquire  \iTrident{} if anyone is foolish enough to withhold it.

\end{document}
