%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nIllicitWeapons{}}

\begin{page}{first}

You need to contact the \pAtlantis{}n mole. Find a way to talk to \cGeneral{} alone and convince him to let you examine the weapons.

Once you have examined the weapons for at least 3 minutes, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

These are definitely the weapons you need. Seal the deal with \cGeneral{}. 

Once you have had the weapons in your possession for at least 10 minutes, turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Maybe you'd better test these weapons out. Go to \sGardens{} and spend 3 minutes shooting the prototype weapon. Role play accordingly.

Once you have finished testing the weapon, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Something doesn't feel quite right. Something is nagging at your mind about the blueprints. Go talk to a weapons expert like \cPrince{}, a mature human, or a powerful magician about the weapons. You will have to show them the prototype and have them examine it for 1 minute. 

Once you have had this discussion, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

They agree that something isn't quite right. But what? Go and do some research in the library and see if you can find any blueprints to compare these to. Spend 1 minute searching each bookshelf in the library. Once you have searched all 3 bookshelves, turn to page \nbref{sixth}


\end{page}

\begin{page}{sixth}

Now that is devious. Only someone as clever as you could have spotted this before half of the \pPacifica{}n army was armed with these time bombs! That \cGeneral{} lied to you. He's been lying to your superiors too. He's no traitor to \pAtlantis{}. How much damage has he already done? How much more might he do? Find some way to end this threat to \pPacifica{}.

\end{page}

\endnotebook

\end{document}
