%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nShipwreck{}}

\begin{page}{first}

If you have a conversation with badge \cGeneral{\MYnumber}, turn to page \nbref{second}.

\end{page}

\begin{page}{second}

That \cGeneral{\mer} seems so familiar. It is stirring something in your memory. Find somewhere quiet and use your Tarot mechanic to get a ``Reading Hand'' consisting of ``The Hierophant'', ``The Hermit'', and ``The Wheel of Fortune''. Close your eyes and mediate on the cards for 1 minute. You may open your eyes at any time, but must start the timer over if you do so. Once you have finished meditating turn to page \nbref{third}.

\end{page}

\begin{page}{third}

Somehow, all of this reminds you of your life on land. But that time was so long ago, and you have trouble remembering details. Go and talk to a human about life on land for 2 minutes to jog your memory. One you have done so, turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Your earliest memories are coming back. \cGeneral{} was your weapons instructor at the palace. But \cGeneral{\they} is supposed to be dead. \cGeneral{} was on the fateful voyage that sank with no survivors, \cKraken{\MYname}. Your father was on that voyage. So what is \cGeneral{} doing in \pAtlantis{}? Go and talk to General \cGeneral{} or Lady \cQueen{} for at least one minute, and try to find out what \cGeneral{\they}'s hiding.  Once you have done so, turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

The pieces are beginning to come together, but only slowly. Go do some research in the library to figure out how \cGeneral{} could be a \cGeneral{\mer} and a human. Spend 1 minute searching each bookshelf in the library. Once you have searched all 3 bookshelves, turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Is it possible that \cGeneral{} is a shape shifter? All of your research suggests that shape shifters are treacherous. You must talk to an expert before you go any further. Discuss the dangers of shape shifters with a priest of the Church of the Tides or a magician for at least 2 minutes. Once you have done so, turn to page \nbref{seventh}.

\end{page}

\begin{page}{seventh}

Definitely treacherous, and dangerous. It is awfully suspicious that this \cGeneral{\human}, if you can even call \cGeneral{\them} a \cGeneral{\human}, is the only survivor of that voyage. A survivor who never returned to \pAmerica{}. You will need to acquire allies and confront \cGeneral{\them} to learn what happened to your father.

\end{page}

\endnotebook

\end{document}
