%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[greennotebook]{NeptuneBall}
\begin{document}

%\item 
%\item 

\startnotebook{\nSpellBreakNotebook}

\begin{page}{first}

Do not open this notebook to page 2 until instructed to do so.

Talk to anyone who's had assassin's guild training on how to get out of magical contracts
Item hunt to get what he needs for the ritual
Get blessing from a Priest, or, if he's dead, the current ruler of Atlantica.
3 people to perform a pactbreaker ritual (requires being knocked out)

\end{page}

\begin{page}{second}

Well, \cManta{} couldn't give you much in the way of specifics, but your talk did do one piece of good. It has reminded you that there were inscriptions on the box. If only you could remember what those inscriptions were. Wait, of course! There must be documentation of the music box in the royal archives. You will just need to do a little research. Spend 1 minute searching each bookshelf in the library. Once you have searched all 3 bookshelves, you may turn to page \nbref{third}.

\end{page}

\begin{page}{third}

You finally found a copy of the inscription in a dusty, forgotten tome. You drew a copy of it, but it doesn't make any sense. Meditate on the inscription for 2 minutes. You must be undisturbed for the 2 minutes or you will have to start over. Once you have had this time to puzzle over the inscription, you may turn to page \nbref{fourth}.

\end{page}

\begin{page}{fourth}

You are brilliant! You figured out that the inscription is actually the lyrics to the tune that the music box plays! It is written in an ancient language that you happen to have studied at the assassin's guild. What luck. Unfortunately, the lyrics are not enough. Go find a musical instrument and at least one person to help you. Spend 5 minutes trying to remember the tune. If you get more people to help you, this will take a shorter period of time. For example, if 2 people help you, it will only take 4 minutes, if 3 people help, it will only take 3. You must have at least one helper though. Once you have remembered the tune, you may turn to page \nbref{fifth}.

\end{page}

\begin{page}{fifth}

That's it! You've got it! How could you have ever forgotten that beautiful melody for a second? Now you just need to dance to it. Find someone else who knows the merengue dance, teach it to someone, or get someone else to teach you another dance, then dance in the great hall to the music from the band. (You can request music for whichever kind of dance you will be doing.) Once you have done so, you may turn to page \nbref{sixth}.

\end{page}

\begin{page}{sixth}

As the last notes of the band fade, you hear another melody. It is faint, and ebbs and flows like the tide, but it is there. The music box! It is playing faintly! You may now interact with the packets on the walls that have musical notes on them. Go to one of these packets and look inside. The arrows will guide your way as you follow the faint tones of music to the room where the music box is. Once you find the room, search for ``\sPacketA{}'', if the music box is in ``\sPacketA{}'', turn to page \nbref{eleventh}. Otherwise, turn to page \nbref{seventh}.

\end{page}

\endnotebook

\end{document}
