\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gAddicted{}}

You are addicted to \iDrug{}. It started as a casual thing with some of your friends in the Guard, but you find yourself craving it more and more. Every couple of hours you have to slip off for a smoke. So far you've managed to conceal this addiction from your parents, and you intend to keep it that way. To that end, you brought a stash with you from the surface. Chewing \iDrug{} is less effective at calming the cravings, but it does work. Unfortunately you failed to account for the lower effectiveness (or possibly your increased need) and did not bring enough to get you through the entire trip. This afternoon, you started to feel the effects of your last dose fade. In your distracted state, you wandered down to the servant's quarters, and came across a young merman chewing what appeared to be \iDrug{}. He offered you a seat, you asked for a bite, and the two of you hit it off immediately.

Your new friend explained that he got his supply from a man who paid for the kinds of thing a servant hears around the palace. He offered to set the two of you up. Finding out secrets in exchange for \iDrug{}? It sounded dangerous, but what choice did you have? You accepted. A few hours later, your friend brought you a list of questions that the dealer wants you to find the answers to.

You arranged to meet the dealer discreetly at \cTFifteen{\MYname{}}, \cTOneFifteen{\MYname{}}, \cTTwoFifteen{\MYname{}} and \cTThreeFifteen{\MYname{}} and pass the answers along to him. He will leave after 5 minutes, with or without his answers. \emph{See the mem-book ``Questions'' for mechanics of this interaction}.

You can feel the bite from this afternoon fading. You will need to take additional hits throughout tonight.
\begin{enumerate}
	\item Within 5 minutes of \cTFifteen{\MYname{}}, you must take 1 dose.
	\item Within 5 minutes of \cTOneFifteen{\MYname{}}, you must take 2 doses.
	\item Within 5 minutes of \cTTwoFifteen{\MYname{}}, you must take 2 doses.
	\item Within 5 minutes of \cTThreeFifteen{\MYname{}}, you must take 3 doses.
\end{enumerate}

If you don't get your doses on time, you start to experience withdrawal. Once you hit withdrawal, you go into a confused rage. You must make a knock out attack on the first person you see with your full CR. If you miss multiple doses, you must attack 1 new person for each missed dose. Once you have attacked as many people as doses you have missed, you must fall unconscious for 5 minutes. Withdrawal applies each hour you don't get your doses.

\iDrug{} has some positive effects and some negative effects. Immediately upon consumption, it will boost your CR by 1 for 10 minutes, but then it will reduce your base CR by 1 for the ten minutes following that. The buffs do not stack or cancel each other out.

{\bf N.B. If anyone in your family finds out about your addiction, give them the mem-packet related to this.}

\end{document}