\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gSpellBreak{}}

You are clinically depressed and under a huge amount of stress at the moment. Your mental state is extremely fragile, and to make matters worse, you have to hide this fact to remain fit as ruler.

You start with a $\Beta$ score of 6, which represents your level of depression. Your score can never go higher than 8, and when it hits 0, you sink into a depression that only large amounts of therapy can help you with. Differing depression levels should affect your roleplaying in different ways:

$\Beta$ 6-8: You have your depression under control. You don't need to act noticeably depressed.
$\Beta$ 3-5: You are starting to spiral into depression. You should show occasional flashes of dark thoughts, and be generally less energetic.
$\Beta$ 1-2: You are on the verge of losing it. Act clearly depressed and seek ways to alleviate your depression as soon as possible.
$\Beta$ 0: You have lost the battle with depression and need professional help. Curl into a ball and talk to yourself for 10 minutes. After this time, your score becomes 1. All future gains, but not losses, to your $\Beta$ are halved.

Here are events that can improve your $\Beta$ score: 

\begin{enumerate}
\item +2 points: Talk to a family member for at least 1 minute. This can only trigger once per half hour, regardless of who you talk to.
\item +2 points: Consume one of your \iTablets{} (destroy it).
\item +4 points: Get the treaty ratified. If this happens in game, this also raises your $\Beta$ score cap by 2 points.
\end{enumerate}

Here are events that can penalize your $\Beta$ score:

\begin{enumerate}
\item -2 points: If you have a fight with a family member.
\item -2 points: Major setback in treaty negotiations (vetoes by the guilds, you fight with Pacificans, etc.)
\item -2 points: See or learn of the death of a guest OR
\item -4 points: See or learn of the death of a family member.
\item -4 points (Post Game): Fail to sign the treaty.
\end{enumerate}

A ruler who has gone into a depressive fit is not fit to rule, so make sure to keep your $\Beta$ score high, especially going into the post game if the treaty is looking tenuous. 

Your \mDepression{} has different triggers that may increase or decrease your $\Beta$ score. These triggers are ingame knowledge for your character. You may strive for them or avoid them as you wish.

\end{document}