\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gLove{}}

You have created a special potion that is unknown to other magicians. This potion causes the victim to become completely enamored of you. They are compelled to assist you in a reasonable manner and not obstruct you in any way. The potion does have some limits though. For example, you cannot compel the victim to kill anybody, although you can order them not to stop you from doing so yourself.

In order to administer the potion, the victim must either be a willing or helpless victim, or you may stick {\bf two} stickers on the target without their knowledge. The {\bf two} stickers must be applied at least 1 minute apart. It does not matter if the first sticker is noticed and removed before the second sticker is applied. The only way to fail in administering a potion is to be noticed while attempting to place either of the stickers.

The potion is PURPLE in color and takes 10 minutes to brew.

The required ingredients are:
\begin{enumerate}
\item A healing potion 
\item A latent poison
\item 2 \iPearl{}s
\end{enumerate}

This potion is brewed as any other potion would be.\\

{\bf How to Brew a Potion:}\\ %%MAKE SIGNS!!!
\begin{enumerate}
  \item Acquire the necessary ingredients.
  \item Stand in front of an unused cauldron for one minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``Full of liquid'' and write down the color of the potion you are brewing.
  \item Return after the duration listed above in the spell and potion list and stir the potion for 1 minute. Put both hands on the sign for this time.
  \item Take the appropriate potion from the envelope below the cauldron, erase the color, and swap the sign back to ``An Empty Cauldron''.
\end{enumerate}
\end{document}