\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gShapeshifter{}}

You have created a special potion that is unknown to other magicians. This potion causes the victim to become a shapeshifter. The victim will be subject to a magical effect of level 5 that can be discovered by another magician with a ``detect magic'' spell.

This potion is particularly finicky. It requires \iHemlock{}, a very rare \pPacifica{}n herb that rapidly looses it's potency. Any sample you obtain in game, or potion you brew from it will expire at \cTThree{\MYname{}}. The potion must therefore be administered before that time if it is to have any effect.

In order to administer the potion, the victim must either be a willing or helpless victim, or you may stick {\bf two} stickers on the target without their knowledge. The {\bf two} stickers must be applied at least 1 minute apart. It does not matter if the first sticker is noticed and removed before the second sticker is applied. The only way to fail in administering a potion is to be noticed while attempting to place either of the stickers.

The potion is GOLD in color and takes 30 minutes to brew. 

The required ingredients are:
\begin{enumerate}
\item \iHemlock{} (\cSpy{} is supposed to be providing you with this)
\item Thing 1 from explorer's guild.
\item Thing 2 rare from caves.
\end{enumerate}

This potion is brewed as any other potion would be.\\

{\bf How to Brew a Potion:}\\ %%MAKE SIGNS!!!
\begin{enumerate}
  \item Acquire the necessary ingredients.
  \item Stand in front of an unused cauldron for one minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``Full of liquid'' and write down the color of the potion you are brewing.
  \item Return after the duration listed above and stir the potion for 1 minute. Put both hands on the sign for this time.
  \item Take the appropriate potion from the envelope below the cauldron, erase the color, and swap the sign back to ``An Empty Cauldron''.
\end{enumerate}
\end{document}