\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gSpellBreak{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

Many years ago, you were put under a spell by a powerful magician, \cWitch{}. You have been struggling under \cWitch{\their} control for quite some time, and have been steadily weakening the curse as time went on. Now the spell is on its last legs, and \cWitch{} is too distracted to properly strengthen it. This is your chance!

Your progress towards breaking the spell is measured in points. You can earn 1 point by meditating for 2 uninterrupted minutes out of the presence of \cWitch{}. This is repeatable, but only once every half hour. Additionally, each of the actions you perform from the list below earns you 2 points towards breaking the spell. Each action can only count once.

\begin{enumerate}
\item Touch the trident for an uninterrupted 10 seconds.
\item Have a magician cast \aLesserDispel{} on you.
\item Drink a Healing Potion (red) when unhurt.
\item Talk to a human about the surface world for 3 minutes.
\end{enumerate}

When you reach 8 points, the spell noticeably weakens. Remove your \iEnslavementSpell{} magical effect. You are no longer compelled to do \cWitch{}'s bidding! But the spell is not fully broken. You are still bound to protect \cWitch{\their} identity by the \iIdentityProtectionSpell{} magical effect.. In order to break the second layer and reveal your former captor, you must complete the steps in the research notebook entitled \nSpellBreakNotebook{}. Open it to page 2.

\end{document}