\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gTarot{}}

You have the ability to use the Tarot to cast someone's fortune. You did not always have this ability -- it developed during your long captivity. You aren't sure whether \cWitch{\MYname} did something to you, or whether this is innate magic power that has bloomed under the ocean, where magic develops much more substantially than on land. Regardless of it's origin however, this ability is incredibly useful. It is certainly part of why \cWitch{\MYname} hasn't killed you yet.

The Tarot is a powerful aid for gathering information, but it is difficult to use without the target's permission. For castings that take less than a few hours to perform, you \emph{must} have the target's permission and cooperation. The quickest casting is a 3 card cast, and is your standard casting.\\

{\bf How to cast someone's Tarot:} %%MAKE SIGNS!!!
\begin{enumerate}
  \item Acquire verbal permission from the target.
  \item Find a quiet place where you wont be disturbed (or overheard), and settle on the floor or at a table with your target.
  \item A good caster always knows \cSlave{\their} target. Roleplay at least 1 minute of discussion with the target to learn about their past, and what they wish to learn about their future. At the end of this time, have the target tell you their ``Tarot'' Score. (The other two necessary cards are listed in the ``\mTarot{\MYname}'' notebook.)
  \item Cast the Tarot:
  \begin{enumerate}
    \item Verify which 2 other cards you need. (Refer to the triggers in the ``\mTarot{\MYname}'' notebook)
    \item Shuffle the Tarot deck 5 times.
    \item Deal out 3 cards.
    \item Set aside any cards you wish to keep. This is your ``Reading Hand'' (You may keep as many as you like.)
    \item Deal out 3 new cards.
    \item Add any cards that you wish to keep to your ``Reading Hand''.
    \item Repeat steps 5 and 6 until you have all 3 necessary cards in your ``Reading Hand''.
    \item Open the associated page of the ``\mTarot{\MYname}'' notebook and {\bf read out loud} what is written on the page. You must deliver this information honestly to your target.
  \end{enumerate}
  \item Pick up the cards, the reading is now complete. You may wish to roleplay giving advice in an attempt to draw additional information out of your target.
\end{enumerate}

You cannot read your own Tarot in game because you already read it pre-game. The spirits were unusually helpful this time, and gave you some useful information about your readings at the ball:

\begin{itemize}
\item The people with the Devil in their draw are all current or former Assassins.
\item The people with the Magician in their draw are all current or potential Magicians.
\item Those with The Lovers in their draw are in a secret relationship with someone.
\end{itemize}

\end{document}