\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gWS{}}

You have chosen to embark on a quest for the fabled wishing stone. This magical artifact is one of the most powerful known under the sea, and can grant many wishes to the one who controls it. The stone does not appear to just anyone however, and you must prove your worthiness.

Answer the questions below, writing down the answer in the space provided. Take the letter indicated in parenthesis after the question, and put it in the appropriate space at the bottom of this sheet. Once you think you know what the letters spell, find a GM and tell them. If you are correct, you will be provided with your prize. If you are incorrect, you must wait {\bf 5} minutes before submitting another answer.

EXAMPLE:
Where are you? (1 word; take the 2nd letter of 1st word)\\
Answer: Atlantica  -- Take ``t''.
		

{\bf Questions:}
\begin{enumerate}
 \item Who gave Poseidon the trident? (1 word, take 1st letter of 1st word) \vspace{5 mm}\\  \underline{\hspace{15cm}}
 \item Between the patron animals of the \pPacifica{}n and the \pAtlantis{}n religions, which is the top predator? (2 words, take 2nd letter of 2nd word)\\ \underline{\hspace{15cm}}
	\item Among the Explorer's Guild, the Guardian's Guild, and the Merchant's Guild, which guild has the oldest current or most recent leader? (3 words, take 3rd letter of 2nd word)\\ \underline{\hspace{15cm}}
	\item Who created the \sArtifactTwo{}? (1 word, take 1st letter of 1st word)\\ \underline{\hspace{15cm}}
	\item Who was the King of Atlantica when the war with Pacifica started? (1 word, take 1st letterof 1st word)\\ \underline{\hspace{15cm}}
\end{enumerate}

{\bf Assemble the letters taken from the answers here (in order):}

\underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}} \underline{\hspace{.5cm}}

\end{document}