\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cAriel{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cSlave}{
  \nickname{Aldric}
  \mapnickinformal
}
You are \cAriel{}, former \cAriel{\Prince} of \pAtlantis{}, and current \cAriel{\King} of \pAmerica{}. You traded your old life away for a chance at love, and now seek to save your family.

Born as the mermaid \cAriel{\prince} of \pAtlantis{} to your \cKing{\parent}, \cKing{\King} \cKing{} and your \cQueen{\parent}, \cQueen{\King} \cQueen{}, your early childhood was a happy one. Your family doted on you, and you were a \cAriel{\prince} - loved by all, and without a care in the world. You loved your little \cPrincess{\sibling} \cPrincess{} from the moment she was born - and for a short time, you were one big, happy family.

That changed abruptly, however, when your \cQueen{\parent} disappeared when you were only 9 years old. The realization that one of your parents was well and truly gone left an unmistakeable hole in your life. Had \cQueen{\they} really loved you? Had \cQueen{\they} left \emph{because} of you? At some level, you knew that these thoughts were ridiculous. At another level, you couldn't get them out of your head.

You started to pull away from your family, from your duties, and distance yourself from them. You couldn't be fully invested here anymore - something had changed. It didn't take long for you to express your restlessness by joining the Explorer's Guild, led by your \cPlant{\Uncle} \cPlant{}. Here, at least, there was a bit of escape. Here, they didn't treat you like a \cAriel{\prince}. Here, you could explore, carefree, and find yourself even as you found treasures in the ruins. It was the perfect escape. You even met your first commoner friend - \cPriest{}, a \cPriest{\priest} of the Church of the Tides. Together, you had many adventures under the sea, and the hole in you heart filled, just a little.

Years passed in relative stability. The memories of your \cQueen{\parent}'s abandonment had all but faded from your mind. It was just a routine exploration - one like any other - when your life changed once again. Alone on an adventure for once, you noticed a ship passing by far above, and against your better judgment, you rose to the surface to see. Upon that ship, high above the waves, you saw a human so blindingly \cEric{\hot} that you nearly choked yourself staring at \cEric{\them} in the open air. It was at that moment that you knew what was missing in your life up until then. You had been born a \cAriel{\mer} when your destiny all along had been to be a human.

The next few days were a blur. You were in a haze of memory so deep and impenetrable that you weren't quite sure HOW you came to be standing in front of \cWitch{}, one of the most dangerous and powerful magicians beneath the sea. But the sight of \cWitch{\them} in all of \cWitch{\their} splendor soon broke you from your reverie.

At first it looked like what you were asking was too illegal even for \cWitch{}, but just when you despaired, \cWitch{\they} agreed to help you. \cWitch{} offered you a ten page contact, which you glanced through. The terms were acceptable, albeit stiff. If you succeeded in finding love within a month, you would retain your legs. If you failed to find true love though, your soul would be forfeit to \cWitch{}. You signed the contract without hesitation. You had no doubt that you and \cEric{} were soul mates and \cEric{\they} would fall in love with you in a heartbeat once \cEric{} met you.

Unfortunately for you, there was some fine print in the contract that you missed on your initial reading. Once you had succeeded in wooing \cEric{}. \cWitch{} slipped into \cEric{}'s castle and revealed your folly. Your success in finding true love saved your own soul, but at the price of you first born \cArielsSon{\offspring}'s soul. You were devastated, but before you could even start to try to negotiate, \cEric{} panicked and called the guards to haul \cWitch{} off to the dungeons. You watched helplessly as \cWitch{} decimated \cEric{}'s personal guard and killed \cEric{}'s \cPrince{\sibling} \cSlave{} by knocking him into the ocean from which \cSlave{\they} never surfaced. \cWitch{} then dove off the balcony into the ocean after \cSlave{\them}. While around you the humans cheered their victory, you were sick at heart. A magician as powerful as \cWitch{}, despite being heavily wounded, was back in \cWitch{\them} element -- it was unlikely that the sharks could finish \cWitch{\them}.

Life on land went on though, and you and \cEric{} were married. You had a \cWillow{\offspring}, \cWillow{} a year later. A few years later, \cEric{}'s father died of old age. It was peaceful, and probably the best thing for him. In many ways the kingdom was more relieved than sad. \cEric{} ascended to the throne, and you became \cAriel{\King}. On land you also learned that a cure exists for \cPolio{}. This crippling disease had begun to affect your merkin in the years before you left. The disease was not yet an epidemic when you left, but there was always that chance, since merfolk had no way to combat it. You worried about your homesea sometimes, but were mostly content.

Well, except for the part where your \cKing{\parent} wont speak to you any more. \cKing{\They} forced you to cut ties with your entire family when you left the sea by disowning you. You miss them, but the happy family you remember from your childhood years was gone long before you left, lost along with your \cAthena{\parent} when you were 9. At least with \cEric{} you have a family with a \cEric{\parent} that didn't sink into endless depression. \cEric{} is there for \cWillow{} in a way that \cKing{} was {\bf never} there for you.

Despite being human, you retained your ability to communicate with ocean creatures. A few years ago, a seagull turned up outside your window with a fish in it's mouth. The fish relayed an urgent message from your contacts in \pAtlantis{}. (Despite your \cKing{\parent}'s best attempts to isolate you for the ``sake of \pAtlantis{}'', you had non-merfolk friends who still kept in touch) Word in the underground was that \cWitch{} had surfaced again, in disguise of course.  Suddenly the old unease over \cWitch{}'s survival bloomed anew. To complicate matters, \cWitch{}'s cover seemed to involve a merchant whose description closely matched \cSlave{}. Is it possible that \cSlave{\they} survived too? 

You immediately went to \cEric{} and discussed what to do. The two of you agreed that you would have to revive your contacts in \pAtlantis{}, to try to confirm these rumors. You'd figure some way out of your contract if it turned out to be true that \cWitch{} was still alive. You reached out to your \cKing{\parent}, apologized a thousand times to \cKing{\them}, and begged \cKing{\their} forgiveness. After only some cajoling, your \cKing{\parent} relented. \cKing{\They} seems to regret the way \cKing{\they} reacted when you left. The two of you talk occasionally at the seashore at the base of your castle.  In the mean time, you banned \cWillow{} from playing in the ocean. If \cWitch{} was still alive, there was no telling what \cWitch{\they} might try to do to get revenge. You had to keep your \cWillow{\offspring} away from \cWitch{}.

It was a few years before \cKing{\King} \cKing{} agreed to let you return to the ocean temporarily. This year is the year. You have two tickets to the \cExExKing{} Ball. Originally, you and \cEric{} were going to attend, but a convergence of things changed that. \cEric{} suddenly came down with an unknown disease.It was somewhat like \cPolio{}, but incredibly rapid and virulent. Within 12 hours, \cEric{} was having seizures and trouble breathing. You would have called off the excursion, but the situation was now dire. You were pregnant again. This time with a \cArielsSon{\offspring}. If you cannot find \cWitch{} and get \cWitch{\them} to rewrite the terms of the contract, you will lose your \cArielsSon{\offspring} \cArielsSon{}.

When you sent word to your \cKing{\parent} that \cEric{} was sick and would be unable to attend, \cKing{} came to console you. You really had been too harsh on \cKing{\them} all those years ago. \cKing{} really did care about you. Unfortunately, \cWillow{} had snuck down to the beach to play in the ocean despite the fact that it was forbidden. \cWillow{\They} saw you talking to \cKing{} and confronted you. Like the troublesome teenager \cWillow{\they} was turning into, \cWillow{} demanded an explanation, and then threw a tantrum that you had hidden something as romantic as the existence of mermaids from \cWillow{\them}. As an attempt to calm \cWillow{}, your \cKing{\parent} offered \cWillow{\them} \cEric{}'s ticket to the ball if \cWillow{\they} would act with decorum.

If only you could tell your \cKing{\parent} that bringing \cWillow{} was incredibly dangerous! Instead, you could only stand helplessly by as \cWillow{} asked an endless stream of questions about \pAtlantis{}.

You and \cWillow{} were escorted to \pAtlantis{} a few hours ago by \cManta{}, your \cKing{\parent}'s oldest advisor, and the only magician still allowed to practice in \pAtlantis{}. \cManta{} cast a spell to allow you and \cWillow{} to breath underwater. As you approached \pAtlantis{}, you noticed something peculiar. The air was full of sounds from the market -- the hustle and bustle of moving carts, voices rising above the current -- but something was missing. You couldn't put your finger on what it was, until \cWillow{} asked you ``Where is the music \cAriel{\parent}? I thought you said merfolk liked to dance?''

\begin{itemz}[Goals]
  \item Find \cWitch{} and figure out how to get out of your contract. (Killing \cWitch{} won't solve your problem as to do so will not void the contract.)
  \item Find out if by some miracle \cSlave{} is still alive. Bring \cSlave{\them} home if you can.
  \item As long as you are here, see if you can dig up any new  clues about what happened to your \cAthena{\parent}. Your sister should be helpful in this matter.
  \item Repair your relationship with \cKing{\King} \cKing{}, and with your \cPrincess{\sibling} \cPrincess{}.
  \item Restore music to \pAtlantis{}.
  \item Keep your \cWillow{\offspring} safe by your side!.
\end{itemz}

\begin{itemz}[Notes]
  \item \pAmerica{} has a long tradition of Swing dancing. If you do not know how to swing, please let a GM know as soon as possible.
  \item You are no longer a member of the Explorer's Guild. Despite knowing it's inner workings, you no longer have access to their supplies.
\end{itemz}

\begin{contacts}
  \contact{\cKing{}} Your \cKing{\parent}. You are still trying to repair your relationship.
  \contact{\cWillow{}} Your \cWillow{\offspring}. \cWillow{\They} is quite a handful.
  \contact{\cPrincess{}} Your little \cPrincess{\sibling}, \cPrincess{\prince} of \pAtlantis{}.
  \contact{\cPriest{}} An old friend of yours, now among the highest ranking Explorer's Guild members. Maybe he can help you?
  \contact{\cPlant{}} Your \cPlant{\uncle} and leader of the Explorer's Guild.
\end{contacts}

\end{document}

