\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cPlant{}}

{\bf You are actually an NPC. You are scheduled to die of poisoning 2 hours into game, in the middle of the banquet.  See a GM before game for details about this.}

You are the only surviving \cPlant{\sibling} of \cKing{}. Your family was slaughtered when you were just a \cPlant{\kid}, and there was nothing you could do to stop it. This trama has left you paranoid, and somewhat schizophrenic. The court physicians long ago certified you insane, which means you aren't eligible to inherit the crown, should anything happen to your \cKing{\sibling}. You are however the leader of the Explorer's Guild. It is a sufficiently prestigious position for a \cPlant{\prince}, but far enough from any real politics to keep you from messing things up. Or so you understand from your \cKing{\sibling}'s explanation.

As leader of the Explorer's Guild, you have spent a lot of time with many of \pAtlantis{}s youth. Your favorite is of course your \cPrincess{\nephew}, \cPrincess{\prince} \cPrincess{}. \cPrincess{\They} is a free spirit, and completely in love. While \cPrincess{\they} think that \cPrincess{\they} can hide it from everyone, it is as plain as day to you that \cPrincess{} is in love with \cDiplomat{}. You would like very much to see these two love birds married, and hang the political fall out if \cPrincess{} doesn't marry the \cPrince{\prince} of \pPacifica{}.

You cannot in good conscience support your \cKing{\sibling}'s endeavor to make peace with \pPacifica{}. You don't trust the people of \pPacifica{} any farther than you can throw them -- any people who would harbor the monsters in the Assassin's Guild don’t deserve any kind of consideration. While you are not involved in the treaty in any official capacity, you do what you can to correct your brother’s doomed course as an unofficial “mediator.” Unfortunately, your bouts of mania make it somewhat difficult to maintain good rapport with everyone involved.

Despite everyone's belief that you are incompetent, you are incredibly perceptive, and can see that many ails trouble \pAtlantis{}. You try to warn people about them, but they seldom listen.

Here are a short list of the things you have been trying to warn people of:
\begin{itemize}
 \item \pPacifica{} has sent a spy to kill \cKing{}.
 \item \pPacifica{} has sent a spy to kill you!
 \item The \cPolio{} vaccine from \pAmerica{} is actually toxic to merfolk.
 \item The Magician's Guild has reformed in secret, and is operating outside of the law.
 \item The mafia is growing incredibly powerful and needs to be dealt with.
 \item \pIndia{} is gathering it's resources to attack \pAtlantis{}.
 \item The black market trade of children that goes on in \pPacifica{} is starting to corrupt the Church of the Tides in \pAtlantis{}.
 \item The Merchant's Guild is looking to overthrow the monarchy and establish a democracy.
 \item The \iWishingStone{\MYname} has reappeared. It appears once every few hundred years, at times of great need.
 \item Shape shifters are actually much more common than the Church of the Tides wants people to believe. They are everywhere! Everyone is in grave danger.
 \item {\bf feel free to make additional things up. You are a little unstable after all. Ask the GMs if you need some ideas.}
\end{itemize}

\begin{itemz}[Goals]
  \item Convince as many people of as many outlandish things as possible.
  \item Actually support \cPrincess{}, your favorite \cPrincess{\nephew}.
  \item Help \cKing{} get the treaty signed.
	\item Prevent illegal magic use through your full authority as \pAtlantis{}n Royalty.
	\item Get your Tarot read. Somehow, you have a bad feeling about today...
\end{itemz}

\begin{itemz}[Notes]
  \item Your catchprase should be something along the lines of ``I'll tell you after the banquet.'' Feel free to invent increasingly ridiculous reasons for why.
  \item You are only somewhat crazy. You should spend about 1/2 of your time perfectly lucid. However, everyone is supposed to believe you are paranoid and your conspiracy theories should not be taken seriously.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cPrincess{}} Your favorite \cPrincess{\nephew}
  \contact{\cKing{}} Your older \cKing{\sibling} and \cKing{\King} of \pAtlantis{}.
  \contact{\cPriest{}} The representative you appointed from the Explorer's Guild whose job it is to see to the Explorer's Guild's interest in the treaty.
	\contact{\cAriel{}} Your least favorite \cAriel{\nephew}. A \cAriel{\mer} who turned traitor by becoming human, and has returned for unclear reasons. Is clearly up to something.
	\contact{\cManta{}} Advisor to the \cKing{\King}. Is clearly up to something.
	\contact(\cQueen{}) A reclusive \cQueen{\mer} who usually keeps to \cQueen{\their}self. Is clearly up to something.
	\contact{\cWitch{}} A very nice \cWitch{\mer} who you often see at various functions. Is clearly up to something.
\end{contacts}

\end{document}
