\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cKing{}}

Ah \pAtlantis{}. Your beautiful kingdom. What tragedy it has seen. First the massacre of your family, then the assassination of \cQueen{\King{}} \cQueen{}, and finally the loss of \cAriel{\Prince{}} \cAriel{}. Sometimes you wonder how it is still a functioning kingdom. Sometimes you wonder how you are still a functioning \cKing{\King{}}.

Your \cExKing{\parent{}} was a good \cExKing{\King{}}. \cExKing{\They{}} brought \pAtlantis{} out of chaos with the help of the \iTrident{\MYname{}} which \cExKing{\they{}} acquired on a dangerous quest many years ago. It was bestowed upon \cExKing{\them{}} by a freshwater spirit. The journey had nearly killed \cExKing{\them{}} -- but it was worth it. The \iTrident{\MYname{}} brought \cExKing{\MYname{}} the power to bring peace to \pAtlantis{}, and secure the borders against the militaristic \pPacifica{}.

You grew up the 3rd \cKing{\offspring{}}, and so never envisioned yourself as \cKing{\King{}}. Instead of studying the ins and outs of politics, you spent much of your youth in the company of the court cartographer. The thrill of the unknown tugged at your heart, and you were never so happy as when you were exploring some uncharted canyon, or previously unknown reef.

Thirty years ago, your carefree life all changed dramatically when \pPacifica{} struck unexpectedly, and slaughtered your family. The only reason you survived was that you had lost track of time while exploring a supposedly bottomless crack in the ocean floor, and so arrived home well after dark. As you swam toward the castle, a sense of uneasiness grew inside you, and a metal taste started to build in your mouth. Sharks circled the palace, making approach nigh impossible for you. When the body of a merperson was thrown unceremoniously out of one of the upper story windows, only to be torn to shreds in an instant, you knew what was happening. No matter how fast the sharks converged, you had seen the flaming red hair of your own mother.

Anger welled up in you and you darted from your hiding place, without a thought in your mind but revenge. It was not until a bolt of electricity shattered the roof of the throne room and your \cExKing{\parent{}}'s \iTrident{\MYname{}} came sailing out of it toward you that the magnitude of what was happening hit you. As your hand closed around the \iTrident{\MYname{}}, you knew you were your \cExKing{\parent{}}'s eldest living heir. The palace was awash in blood, both \pPacifica{}n and \pAtlantis{}n that night. 

A growing dread, your own adrenaline, and the lurking nightmares that threatened to swallow you kept you from your rest that night. In the deepest hour of the night, a \pPacifica{}n army attacked, expecting to find \pAtlantis{} in disarray. Instead, they met the tip of your \iTrident{\MYname{}}, and that of your soldier's weapons as well. You drove the army out, showing no mercy, and pursued them deep into \pPacifica{}. In your rage and shortsightedness, you ordered fields and homes destroyed, families killed and livelihood's decimated. You wanted \pPacifica{} to truly feel the pain that tore at your own heart.

Upon returning to \pAtlantis{}, you felt empty. There was no sense of satisfaction--no closure. You tried to rebuild what \pPacifica{} had so callously destroyed. After a year of mourning,you took a \cQueen{\spouse{}}, \cQueen{\King{}} \cQueen{} in an attempt to raise the spirit of your people. \cQueen{\They{}} was beautiful, kind, and tried to help you to put the past aside gently and live again. Despite the life you built with \cQueen{}, and your 7 beautiful children, your past haunts you. You deeply regret the revenge you extracted against \pPacifica{}. 

Then \cQueen{} was killed. You missed her at breakfast one morning, and when you went to her chambers to awaken her, for surely \cQueen{\they} had just overslept after the long sea-horse ride the two of you had taken the day before. When you opened the door to her chambers however, you were met with a horrific site. The entire room was in shambles, with many of her greatest treasures shattered. Since there was no body, you maintained hope that she might still be alive, only kidnapped for ransom. You squandered a large part of the royal treasury on unsuccessful searches for \cQueen{\them{}} kidnappers. After almost a year, you had to concede defeat. Your beloved \cQueen{} was dead. You looked around you at \pAtlantis{}, and felt like you had failed her. Your beautiful country, which you were never meant to run. The gloom of worthlessness washed over you.

It was almost the last straw when \cAriel{\Prince} \cAriel{} abandoned \pAtlantis{} for the human world. That was 11 years ago.  It wrenched your heart to lose \cAriel{\them{}}. Worse than just losing her, if word got out that contact was possible with the human world, who knew what changes might come to \pAtlantis{}. The destruction that humans were capable of wreaking on your world was incalculable. \cExKing{\King} \cExKing{} had never trusted them, and neither do you. You bent all your power on hushing up what you could, (you dissolved the Magician's Guild, suspecting that one of their members had been involved) but there was no way to cover the gaping hole in your heart, and that of \pAtlantis{}. Your bitter last words to \cAriel{\Prince{}} \cAriel{\MYname{}} still poison the taste of food in your mouth. If only you could make it up to her. If only you could apologize, then things could be the way they were. But \cAriel{\they{}} had no idea what destruction \cAriel{\they{}} might have brought down on \pAtlantis{}.

In your darkest hour, the spark of hope wormed its way into your mind: peace. That is what you could offer \pAtlantis{}. That is how you would have your reign remembered. Not in tragedy, and blood, but in peace and hope and renewal. It was as if you were a new person, looking out on the world. Peace with \pPacifica{} - that was your guiding light. You sent emissaries, and opened communication channels. Hope swelled in your chest, and life was worth living again. Then talks stalled. \pPacifica{} claimed that had apprehended spies from \pAtlantis{} at it's borders. Unfortunately for you, your youngest daughter \cDaughter{} was caught among them. She showed herself to be an unexpectedly brilliant diplomat however, smoothing the whole issue over with a dramatic tale of love and longing for the unknown world of \pPacifica{}. Talks proceeded with new vigor, and optimism.

To complete the absolute reversal of fortune, after ten years apart, you sort of reconciled with your estranged daughter.  You learned that \cAriel{} had a an 8 year old child. Now, only a year after that, \cAriel{\MYname{}}, \cAriel{\their{}} \cEric{\spouse}, and \cAriel{\their{}} \cAriel{\offspring{}} have agreed to attend this year's \cKing{}'s Ball. 

The treaty with \pPacifica{} was drafted, and will be signed at a special ceremony during the Ball tonight. The treaty has been five years in the making and will be your crowning achievement. Nothing must be allowed to sabotage this treaty.

\begin{itemz}[Goals]
  \item Get the peace treaty signed.
  \item Reconcile with \cAriel{\MYname{}}.
  \item Ensure your guests have a good time.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cAriel{}} Your estranged daughter
  \contact{\cEric{}} \cAriel{}'s \cEric{\spouse{}}, and \cEric{\Prince} of the humans.
  \contact{\cManta{}} Your trusted advisor. \cManta{\They{}} has been with you since the raid on \pPacifica{}.
\end{contacts}

\end{document}
