\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cManta{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

Where to begin? The beginning is so far in the past, it's hard to trace the convoluted path that has led you to this day. You guess it all began with \cExExKing{\King} \cExExKing{}, \cExExKing{\King} \cKing{}'s grand\cExExKing{\parent}, and your \cExExKing{\parent}. Although can you really call \cExExKing{\them} your \cExExKing{\parent}? \cExExKing{\They} never accepted you, never acknowledged you, never did anything for you.

\cExExKing{\They} was jealous of \pPacifica{} in every way. From the bounty of the harvests on the Central Pacific Basin, to the beauty of the kingdom's only \cMother{\prince}, your \cMother{\parent} \cMother{\MYname}. \cExExKing{} started a war over it. A war that devastated both \pPacifica{} and \pAtlantis{}. In the end, he got what he wanted though. His aggressive military tactics led to a breech in the castle wall, and the successful capture of your \cMother{\parent}. \cExExKing{} carried \cMother{\them} off, back to \pAtlantis{}, and by the time a successful counterattack was mounted to retrieve her, you had already been conceived.

Your \cMother{\parent} burned for revenge. \cMother{\Them} brothers wished to just kill the child and pretend as though you had never been. But your \cMother{\parent} was cleverer than they could ever hope to be, and persuaded \cMother{\them} brothers to spare your life, but put out the word that you had died.

And so you were raised in secret, at \pAssassin{} where you and your \cMother{\parent} were hidden away. The only thing that grew faster and stronger than you was your hatred of \pAtlantis{} and what \cExExKing{} had done to your \cMother{\parent}. \cExExKing{} had to pay. When \cExExKing{\they} died in battle when you were 5, you were not deterred. \cExExKing{\Their} decedents, including \cExKing{}, carried the same sin in their veins. Their blood would also quench your thirst for revenge. Although your \cMother{\parent}'s seer's gift pass only through the female line, you were not without your own talents. From a young age, magic flowed in your veins, and you studied hard from the moment you could read.

At the age of 14, you set out on a quest to find \iTrident{\MYname}. \cMother{} had a vision that the fate of both \pPacifica{} and \pAtlantis{} were intimately tied to it's fate, and despite your youth, you relished the chance to strike back at your \cExExKing{\parent}'s country. Besides, with an artifact as powerful as \iTrident{\MYname}, you could take your rightful place on the throne of \pAtlantis{}. After all, \cExExKing{}'s blood ran in your veins as strongly as it ran in \cExKing{} and you were conceived first. You were the elder \cManta{\offspring}. The throne was yours by right. The search took you 20 years, was dogged by bitter tragedy, and ended in temporary -- albeit extended -- failure. 

Perhaps the bitterest moment whas when your \cMother{\parent} died, alone, while you were fighting for your life in the freezing waters of the Ross Sea. In the end it turned out to be a bad lead anyway. Your intelligence next led you to \pAtlantis{}. With a few words whispered in the right ears, you persuaded \pPacifica{} to attack the Angola plain of \pAtlantis{} by sneaking through the neutral kingdom of \pIndia{}. The operation gave you the perfect cover as you blended in with a group of \pAtlantis{}n refugees. This time, the move almost paid off. You established yourself in court, and made your extensive magical powers available to the then current \cExKing{\King}, \cExKing{}. You rose through the ranks in court, as well as in the Magician's Guild. You were soon among those elected to the Court of Advisors, with easy access to the \cExKing{\King}s ear. This put you in the crucial position to continue your search for \iTrident{\MYname}.

It took you 14 additional years, but you eventually traced the trail of  \iTrident{\MYname} to the fjords of Norway, and a nixie by the name of \cNixie{}. Unfortunately \cExKing{} got there first. He persuaded \cNixie{} to give him the \iTrident{\MYname}. You watched from a convenient cave as he swam away. You fantasized about blasting him out of the water with a particularly vicious spell, but with \iTrident{\MYname}, he would certainly have bested you in the fight. It was not yet time to show your hand.

You slunk back to \pAtlantis{}, and waited. You studied the problem from every angle, but there didn't seem to be a way around the problem of \iTrident{\MYname}. Your best hope was to somehow be named the legitimate heir to the throne. The \cExKing{\King}'s brat, \cKing{} didn't help the problem. Most would have despaired at that point, but you were a patient mer\cManta{\human}. Here was another chance to ruin \cExExKing{}'s line. You arranged to have a baby \pAtlantis{}n \cQueen{\kid} kidnapped and taken to the Assassins Guild for just such an occasion. There \cQueen{\they} was raised and trained as the perfect match for \cKing{}. When \cKing{} was just old enough to take the throne, you smuggled a dozen \pPacifica{}n assassins into \pAtlantis{} to kill the royal family. \cKing{} was \emph{conveniently} off on an Explorer's Guild expedition. Again, many might question your logic -- why not have the assassins kill \cKing{} too? Your long game wasn't mature yet though. Proof of your lineage was frustratingly hard to come by with your mother and father both dead. You couldn't risk the kingship passing too far from the \cExExKing{} lineage, otherwise you might lose your claim to the throne.

Converted to a sleeper agent with a fairly complex memory suppression spell, you integrated \cQueen{}, the kidnapped baby mer\cQueen{\kid}, in the \pAtlantis{}n court. At least that part of the plan seemed to go off well, and within a year, \cKing{} was married to \cQueen{}. Of course, they then had a \cAriel{\offspring}. Maybe you should have killed \cKing{} when he was a baby? This was getting complicated.

While you secretly manipulated \cKing{\King} \cKing{}'s life, you continued to tend your other plans. Among them was the Magician's Guild. You maintained your position as elected representative to the Court of Advisors, and cultivated your standing with other magicians. One particularly powerful contact was \cWitch{}. \cWitch{\They} gave you an anti-aging spell that if properly maintained meant you could essentially live forever. At the age of 52, you stopped aging.

Things settled down in \pAtlantis{} after that. For a couple of years, things were stable. Then that stupid nixie decided to get involved again. You felt the brush of her power, late one night about 20 years ago. You traced the ``scent'' of it through the palace, like a shark on a blood trail. You found yourself in front of \cQueen{}'s room. You envisioned of your carefully laid plans unravellings as \cNixie{} whispered the truth to \cQueen{} in dreams. You burst into the room, fear throwing caution to the currents. But there was no catastrophe waiting for you on the other side of the door. \cQueen{} slept soundly and the residue of \cNixie{} was already diluting. Still, when \cQueen{} slipped off in what \cQueen{\they} thought was a sneaky manner the next morning, you resolved to put this part of your plan into action.

A few weeks after \cQueen{}'s return, you unraveled the spell that locked away her memories. You cloaked yourself in darkness, rendering yourself nearly invisible -- at the cost of several brutally finicky potions -- so you could watch and savor the moment of betrayal that would course through \cKing{} before \cQueen{} killed him. But you waited in the \cKing{\King}'s chambers in vain. \cQueen{} never came to fulfill her mission. The next morning you learned that \cQueen{\they} was gone, and her room destroyed. The minx had stagged \cQueen{\them} own kidnapping and got away with it. You lost track of \cQueen{\them} for a few years.

In the mean time, there were other matters to deal with, including \cAriel{\Prince} \cAriel{}, who managed to persuade some magician to turn \cAriel{\them} into a human. This set \cKing{} off on a tirade that ended with him disbanding the Magician's Guild. The guild was scattered, magic was banned, and your position in court was suddenly very tenuous. Around this time, \cWitch{} disappeared as well. You figured \cWitch{\they} was involved in some way when \cWitch{\they} came to you a few weeks later, gravely wounded and need of secret aid. \cWitch{\They} had with \cWitch{\them} a human \cSlave{\Prince}. \cWitch{} was so weakened that \cWitch{\they} needed your help concocting a powerful enough love potion to suppress \cSlave{\their} will and make \cSlave{\them} \cWitch{\them} slave. If only you'd remembered to write it down! Alas, a missed opportunity

And there there was the matter of the \iMusicBox{\MYname}. This innocuous looking trinket that \cQueen{} had brought back from \cNixie{}. It played a song of protection for \cKing{}'s line, and for \pAtlantis{}. As long as this box existed, it was a threat to all of your carefully laid plans. It was clearly a powerful magical item equal almost to the \iTrident{\MYname}, for when you tried to destroy it, your ever attempt was thwarted. It took 11 years before you were even able to steal it from it's pedestal in the royal treasury. You hid it away in the castle and schemed about how to destroy it. It was clearly losing power. It needs to be maintained ever couple of years or it would slowly wind down. You calculated the rate of decay over and over. The spell will finally be weak enough for you to destroy the box tonight.

\cWitch{} turned up again, this time in the guise of \cWitch{\MYname}. You and \cWitch{\they} put feelers out in the underworld, and slowly built the Magician's Guild back up as a secret society. Not all magicians would have kept the secret though, and you had to be careful. Still, it was good to be back among other magicians. It weighed heavily on you that there was no way to contact the \pPacifica{}n counterpart to the Magician's guild reliably. You got one message through, telling them that you had revived the Guild in \pAtlantis{} and that was it.

In a stroke of luck, one of the magicians had word of \cQueen{}. He didn't know it was her of course, but the timing of \cQueen{\them} appearance, and \cQueen{\them} visage was enough to convince you. As the pieces for tonight began to fall into place, you wrote an anonymous letter to \cQueen{}, enticing \cQueen{\them} back to the court with lies about an assassination plot against \cKing{}. You wrote to the Assassin's Guild and they have sent an assassin to do away with \cQueen{}. Eliminating \cQueen{} will simplify your ascension to the throne. Assisting in \cQueen{\them} assassination is in your best interest.

Tonight is the \cExExKing{}'s Ball. At the Ball, \cKing{\King} \cKing{} intends to sign a treaty with \pPacifica{}. You would rather that \cKing{} did not achieve peace. Much better if you can reserve that for after you take control. That way, \emph{you} will be hailed as the hero of \pAtlantis{}. To prevent \cKing{} from attaining peace, you will have to find a way to torpedo the treaty tonight. As an added bonus, it may also drive him over the brink of insanity. An insane \cKing{\King} is not fit to rule, and it is one way to remove people from line of succession without killing them -- and bringing sharks down on your head.

The Assassin's Guild is also not terribly enamored of the idea of peace between the countries. They have therefore sent \cSpy{} to help you out. You met up with \cSpy{\them} last night to fill \cSpy{\them} in on the most recent happenings in the negotiations. If only \cSpy{} were not an incompetent idiot.  \cSpy{\They} was also supposed to bring you some \iHemlock{\MYname}, a rare ingredient that is key to your hallucination serum. The \iHemlock{\MYname} is only fresh for a few days, and \cSpy{} left it in \cSpy{\them} room last night. You will have to make the exchange tonight, and then brew the potion in the palace! There will really be no talking your way out of it if you are caught with either the \iHemlock{\MYname} or the resultant potion.

Tonight will be a careful dance. You need to prevent the treaty from happening and destroy the \iMusicBox{} tonight. You may not have another chance at either of these. The rest of your plans are not so immediate. It would be convenient to complete as many parts as possible, but you \emph{cannot} afford to have your ultimate plans revealed. Better to spend the night under the radar. Just act the loyal advisor, and pretend help \cKing{} ensure all his guests have a good time.


\begin{itemz}[Goals]
  \item Sabotage the Treaty. It is \cKing{}'s dream and it's failure very well may drive him over the edge into madness.
  \item Prevent \cPrincess{} from marrying anyone. As the \cKing{\King}'s advisor, \cPrincess{\they} will be obligated to marry you next month when she comes of age if there are no other approved suitors. This would put you first in line for the throne.
  \item Keep your membership in the Magician's Guild a secret -- or get \cKing{\King} \cKing{} to lift his ban on magic.
  \item Destroy the \iMusicBox{}. You've stashed it in $<$insert location$>$ and need to keep it hidden from prying eyes until 3 hours into the game when the spell will be weak enough to destroy it.
  \item If the opportunity arises, find proof of your lineage and attempt to seize the throne by killing or discrediting those ahead of you in line.
  \item Acquire the \iHemlock{} and brew as many hallucination potions as you can.
  \item Investigate rumors of a \iGlowShell{\MYname} in the palace. If you can acquire it, it will greatly boost your magical powers.
\end{itemz}

\begin{itemz}[Notes]
  \item Having been raised at the Assassin's Guild complex, you know that all agents from the guild are suppose to bear a tattoo on their left bicep. You were never officially part of the Guild however, and therefore bear no such brand.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cKing{}} Your nephew and the man who is sitting on your throne.
  \contact{\cWitch{\MYname}} This is \cWitch{} in disguise. \cWitch{\They} is a powerful magician and may prove a crucial contact.
  \contact{\cPrincess{}} \cKing{}'s younger \cPrincess{\offspring} and heir to his throne.
  \contact{\cPlant{}} \cKing{}'s younger \cPlant{\sibling}. He is more than a little crazy and is always yammering about conspiracy theories.
  \contact{\cQueen{\MYname}} This is \cQueen{} in disguise. You have no intention of revealing that you know \cQueen{\them} unless strictly necessary.
  \contact{\cSpy{}} Your \pPacifica{}n contact who is bringing you \iHemlock{} and is supposed to help you sabatoge the treaty.
\end{contacts}

\end{document}
