\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cSpy{}}

Your name is \cSpy{}. You are a spy sent by the Assassin's Guild on a mission to collect intelligence, protect \pPacifica{}'s interests, and prevent the signing of the treaty by any means necessary.

Your early childhood was a fairly normal and happy one. Your family was atypical only in the fact that your parents managed to have two healthy children when so many families had none, and the two of you got along well. That normalcy was quickly shattered, however, when you were kidnapped on your eighth birthday, and whisked far away to the icy waters of the Bering Strait to begin your new life as an assassin.

Like all displaced children, you fought your new life at first. The Assassin's Guild was austere and unforgiving - mistakes were punished swiftly and harshly. But slowly, over time, you began to appreciate the sense of power that your new life brought to you. You were stronger, faster, sharper, and improving your body and mind had always appealed to you. By your fourth year, you had fully embraced your new lifestyle, and were well on your way to becoming a deadly, invisible force. You graduated with full marks as an infiltrator with an unflinching dedication to your guild.

Reintegrating into society and your family was easier than you had expected. Your cover story was that you had been kidnapped by the \pPacifica{}n child black market and had trekked across the country after your foster family revealed your lineage to you. You were never quite sure if your parents fully believed your story, but your \cBodyguard{\sibling} \cBodyguard{} certainly did. You hadn't made any friends in the Assassin's Guild, so the companionship of your younger \cBodyguard{\sibling} was a welcome change. Sadly, your duties called, and too soon, you had to move away to take up a diplomatic post at the \pPacifica{}n Royal Palace, where you could only visit \cBodyguard{\them} occasionally. You did manage to secretly pull some strings with the Assassin's Guild to get \cBodyguard{\them} transferred out of military training into a safer bodyguarding role, however, so at least you won't have to worry about \cBodyguard{\them} dying in a border skirmish.

Two weeks ago, you were contacted by your Assassin's Guild superiors with a job. The Assassin's Guild has a different view of the future of \pPacifica{} from the royal family, and it doesn't involve a treaty with \pAtlantis{}. Therefore, you are to attend the treaty negotiations soon to occur in \pAtlantis{} and in your role as diplomat, prevent and obstruct the treaty from being signed. Meanwhile, you are to meet the \pAtlantis{}n General \cGeneral{} to inspect and, if all was in order, arrange the sale of a new type of weapon that would give \pPacifica{} the edge in the coming war. Your second contact is \pAtlantis{}n Court Advisor \cManta{}, who has requested some rare and dangerous herbs, which the Assassin's Guild went through some trouble to obtain. \cManta{\them} will provide information and support for you in exchange. 

Receiving this assignment immediately gave you an idea. As a dabbler in military history, you are intimately familiar with the \pPacifica{}n view of the origins of this war, and though much of it has been lost to time, you have the distinct feeling that \pPacifica{} wasn't the aggressor as \pAtlantis{} has always claimed. A meeting with \CManta{} last night about your future plans gave you the first beginnings of the story, and what he told you was quite interesting. Additional research in the \pAtlantis{}n royal library is definitely in order - and maybe what you uncover can help you more easily sabotage the treaty. 

Last week, amidst your preparations for your departure, you collapsed on the sidewalk as you were returning to your home. A trip to the doctor quickly revealed the worst - \pPolio{}. You had been living with it all of your life, and you never knew - and at this point, it could kill you within months. This left you with a problem - sabotaging the treaty would prevent \pPacifica{} from receiving a cure in the short term. Conquering \pAtlantis{} would serve the same purpose, but at this advanced stage of your disease, you might not live to see that come to pass! You know that humans are the source of the cure, and this is the only time you're likely to interact with humans on friendly terms in the near future. Maybe the human delegation can be of some use to you...

\begin{itemz}[Goals]
	\item Prevent the treaty from being signed
	\item Find the hidden history of the war, which may help spark tensions between the two parties
	\item Avoid being outed as a member of the Assassin's Guild, and avoid capture at all costs
  \item Find any military intelligence you can about Atlantica to report to your superiors for the eventual war
	\item Investigate the \iPrototype{} and seal the deal if it is viable
	\item Deliver the herbs to \cManta{}, and extract information from him in exchange
	\item Find a cure for your \pPolio{}

\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
	\contact{\cDiplomat{}} The diplomat in charge of the \pPacifica{}n delegation.
	\contact{\cPrince{}} The \pPacifica{}n \cPrince{\Prince}.
  \contact{\cBodyguard{}} Your \cSpy{\sibling}, who you love and can rely on.
	\contact{\cManta{}} Court adviser to \cKing{\King} \cKing{} and known magician.
	\contact{\cGeneral{}} Your weapons supplier.
\end{contacts}

\end{document}
