\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cPrincess{}}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

You are an \pAtlantis{}n \cPrincess{\prince} who loves \cPrincess{\them} \cKing{\parent}, \cPrincess{\them} country, and \cPrincess{\them} forbidden inamorato across the border in \pPacifica{}. You love to dance, love to explore, and tolerate diplomacy only for how it serves your other loves in life.

Born an \pAtlantis{}n \cPrincess{\prince}, your life should have been a dream. But you had to endure the pain of growing up without a \cQueen{\parent} for all these 23 years. You are told \cQueen{\they} left when you were two. It doesn't really matter though, because you don't remember \cQueen{\them} at all. Growing up, you often dreamed that your \cQueen{\parent} was still alive, and would just turn up one day, and everything would be perfect. If only life were so sweet.

Growing up without a \cQueen{\parent} has been challenging, but you spent a lot of time with your \cPlant{\uncle} \cPlant{}, head of the Explorer's Guild. You may even be more fond of your \cPlant{\uncle} than of your own \cKing{\parent}, since \cPlant{} always made time for you. You don't care that everyone thinks \cPlant{\they}'s crazy. \cPlant{\Their} wild conspiracy theories are kind of endearing. And who knows, maybe \cPlant{\they}'s even right about some of them.

You might have been able to cope with your \cQueen{\parent} leaving you, if not for your \cAriel{\sibling} following in \cQueen{\them} footsteps when you were 10. \cAriel{} left for the human world via the darkest of magic (according to your \cKing{\parent} anyway). \cKing{\They} never really spoke of \cAriel{\them} again, but you noticed he was taking higher doses of his medication after that.

Of course your \cKing{\parent} doesn't know that you know about them, but you've know for as long as you can remember that your \cKing{\parent} has been struggling with depression. You've made an effort to help \cKing{\them}, by covering for \cKing{\them} whenever possible, and trying to show \cKing{\them} that you at least care. You are very subtle about it though (for the sake of \cKing{\their} pride), and have so far avoided tipping \cKing{\them} off that you know anything about it.

But enough about your family, most of whom don't care about you. You spent your teenage years learning to dance. Whenever your \cKing{\parent} would forbid you to leave on an Explorer's guild trip

You spent many of your teenage years either cooped up in the castle, enduring stupid lessons about diplomacy, or out with the Explorer's Guild and your \cPlant{\uncle}. Although time away from the castle was nice, you really didn't have anyone you could trust -- at least until you met \emph{\cDiplomat{\them}}.

You had gotten back late from an Explorer's Guild trip, and were making your way down to the kitchens for a late night snack when you literally ran into \emph{\cDiplomat{\them}}. Time stopped. You stared into each other's eyes for a heartbeat -- then two. You looked down shyly. You were grimy from a day of exploring, your bag still slung over one shoulder, and your jacket covered in mud. You tried to stammer out an apology at the same time as \cDiplomat{\they} did. After a moment, you recovered your poise and asked ``Would you like to join me in the garden?'' \cDiplomat{\They} said ``yes,'' and the rest was history.  It turned out that \cDiplomat{\they} was a \pPacifica{}n diplomat named \cDiplomat{}, and the two of you can't see enough of each other. 

You started taking an interest in politics as an excuse to try to see \cDiplomat{\them} more often. When that wasn't often enough, you started sneaking across the \pPacifica{}n border with your friend \cPriest{} from the Explorer's Guild. It didn't hurt that you were assisting in a noble cause. \cPriest{} has been working for years to find homes in \pPacifica{} for \pAtlantis{}n orphans. You never could understand why it was illegal.

You always knew sneaking across the border was risky, but it all seemed so abstract until it finally happened. Your routine visit got you caught by the border patrol, led by the crown \cPrince{\Prince} \cPrince{\them}self. You and \cPriest{} were escorted back to the \pPacifica{}n capital, and into the castle itself. There you were interrogated, albeit politely, for what seemed like days by the \cPrince{\prince}. It was quite the dance for you to avoid revealing anything important. Just when things seemed darkest, \cDiplomat{} appeared. With a few well placed whispers in the ear of the \cPrince{\Prince}, \cDiplomat{\they} set in motion your release and safe return to \pAtlantis{}.

Your \cKing{\parent}, \cKing{\King} \cKing{} grounded you for several natural lifespans upon your return. Apparently getting caught in enemy territory is not something a \cPrincess{\prince} is supposed to do. Your \cKing{\parent} would prefer you stayed grounded, and out of the public spotlight, for a very long time, but the \pPacifica{}ns repeatedly requested to work with you. That was almost certainly \cDiplomat{}'s doing. 

With the fiasco that resulted from getting caught, it is clear that you won't be able to sneak over the border any more. Your \cKing{\parent} will be watching you like a shark. You have to find some legitimate means to see \cDiplomat{}. The treaty would actually simplify things a lot because if \pPacifica{} and \pAtlantis{} could be brought closer together, free movement across the border would be possible. On the other fin however, \cKing{\King} \cKing{} has been contemplating marrying you off to the \cPrince{\prince} of \pPacifica{}. That would be a problem.  If you can't get out of that, as a last resort, you could try to elope with \cDiplomat{}. You are pretty sure \cPriest{} could perform the wedding.

With the \cExExKing{} Ball approaching, \cDiplomat{}, the \cPrince{\prince} and a small entourage of \pPacifica{}ns have been staying at the palace. Last night, you and \cDiplomat{} stayed up late talking. It's nice to talk to him, he always listens to you. Especially when you need to rant about your \cQueen{\parent}. Unlike your \cKing{\parent} and most of \pAtlantis{}, \cDiplomat{} doesn't believe the official story that your \cQueen{\parent} was kidnapped and killed by \pPacifica{}ns. \cDiplomat{\They} has found no proof in the extensive records of \pPacifica{}. Instead, he agrees with your theory that \cQueen{\King} \cQueen{} simply abandoned you in your early years and went off to who knows where, to do who knows what.  Since a bunch of guests from far flung parts of \pAtlantis{} will be at the Ball, you have some hope of gathering clues. It is a long shot, but maybe somebody has heard something. Your \cAriel{\sibling} \cAriel{} is probably your best bet. Also you haven't talked to \cAriel{} in a very long time, and she deserves a piece of your mind for leaving you.




\begin{itemz}[Goals]
  \item Blah
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{}
\end{contacts}

\end{document}
