\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cWitch{}}

\updatemacro{\cWitch}{
  \nickname{Ursula}
  \mapnickinformal
}

\updatemacro{\cSlave}{
  \nickname{Aldric}
  \mapnickinformal
}

\bigquote{``Pearls before Swine''}

Beauty and Power. Those wonderful, tempting, wretched things. Beauty and Power have defined your entire life. They are liberation and confinement, the bait and trap, a gilded cage you couldn't resist.

You are the paragon of beauty, and have been for almost 60 years. As a young \cWitch{\mer}, you were the belle of your town. From the time you began to flower into \cWitch{\human}hood, until your 18th birthday, you were elevated as the most beautiful \cWitch{\mer} anyone had ever seen. Every year at the midsummer festival, you were crowned as \cWitch{\King} of the festival. You loved the attention and the flattery, and your ego grew uncontrollably.

On your 18th birthday, the day of the midsummer festival, everything started to go wrong. You decided to get a reading from a quarent tucked away in a corner of the fair. You'd seen him in previous years, but had never worked up the courage to approach him. Your curiosity finally mastered your fear though, and you darted into the tent. Scents in the water, contained by the fabric of the tent and a fair bit of magic, assailed you. You felt light headed, and almost backed out, but you couldn't figure out where the door was. Actually, you couldn't remember why you were there at all until the old man asked you if you wanted a reading.

You nodded and settled shakily into a chair. Then the old merman cast your cards -- The High Priestess, The Hanged Man, and Judgment -- and spoke the words you feared the most.

You were devastated. The future predicted for you was terrible. Fade into anonymity? You think not! When the old man slyly mentioned a way to avoid this fate, you jumped at the chance. Perhaps the fumes in the tent were really getting to you, because you would later regret this decision bitterly. The old merman offered you \iAmulet{\MYname}. The amulet is a portal to \emph{the other side}. There are powerful spirits there, that can grant any wish. You immediately grabbed the amulet and demanded eternal youth and beauty. You then cursed your competition for the beauty pageant, just for good measure. You swam away from the quarent's tent, the amulet around your neck, flushed with victory. 

It wasn't until a few weeks later that the dreams started. Terrible \emph{things} invaded your dreams. The spirits from the other side whispered in your ear, screamed in your face, and tormented your every sleeping moment. You slept for days, trapped in the dark, horrid twilight, where the fabric between this side and the spirit world is thinnest. The spirits demand payment for the favors they had granted you. After impressing upon you the terrible fate awaiting you, should you fail to repay your debt, the spirits released you back to the living world. Your task -- to acquire as many souls as possible for the spirits -- would be aided by your ability to call upon the spirits' power, but you had to be careful that you worked your way \emph{out} of their debt. You always have to get a good deal for any spell you provide someone, else you will find yourself deeper in debt.

You quickly abandoned your home town, traveling \pAtlantis{} as a gypsy. It was your only real chance to trick people into giving up their souls for as little as possible. You learned to read people quickly, and to be a high stakes gambler. It usually paid off handsomely. Despite this, it was slow going. The anti-age wish you had made had an upkeep cost, and there was no un-doing it. For 50 years, you struggled to repay your debt to the spirits. In the process, you gained a reputation as a powerful sorceress, and rose through the ranks of the Magician's Guild. Unfortunately you aren't a \emph{real} magician. All of your power comes from the spirits on the other side, and any time you are asked to prove your magical ability just drags you deeper into debt. It is expensive to be thought of as a powerful magician. And yet, the thrill of being feared and worshiped and looked up to and consulted about things was addictive. You could never find the right time to step down from your position in the Guild.

To your great surprise and pleasure, about 15 years ago the seemingly perfect solution swam into your cave. \cAriel{\Prince} \cAriel{} came to you, asking to be turned into a human. Contact with the human world was forbidden, even at that time, so \cAriel{} was understandably nervous. You took your time consulting with the spirits and finally came to a decision. For such a dangerous and powerful spell, you would accept only the eternal soul of someone of royal blood. The spirits promised you that the soul of a royal child would be enough to erase your debts completely. Despite the risks to yourself -- the spell would cost you dearly -- you took it. The chance to be free forever was too tempting to pass up. You offered \cAriel{} this deal: If \cAriel{\they} found true love within a month (a laughably short window) \cAriel{\them} soul would be safe, but if \cAriel{} failed to find true love, \cAriel{\them} soul would be forfeit to you. Just for security, you slipped in one other clause: should \cAriel{} manage to find true love, the soul of her first born \cArielsSon{\offspring} would be forfeit instead. \cAriel{}, out of her mind with desire to experience the human world, signed the contract with barely any hesitation. You were confident you would be free and clean of the spirits in a month.

This time, your luck betrayed you. Your high stakes gamble was quickly put in jeopardy as \cEric{} fell in love with \cAriel{}, and within a few short weeks, began planning their wedding. You had to consult the spirits to be sure, but it was in fact true love. \cAriel{} had upheld \cAriel{\them} end of the bargain and the prospect of waiting for \cAriel{\them} to have a \cArielsSon{\offspring}, which might take years, or even never happen, infuriated you. This was not supposed to be a gamble. A month to find true love? It was nearly impossible. This was supposed to be easy. Why could things never be easy?

You had a bad feeling about this now, and went to the surface to remind \cAriel{} about the fine print. You disguised yourself as a servant and slipped into the castle. You worked your way into \cEric{}'s private chambers, and revealed to \cAriel{} and \cEric{} that in order to become human, \cAriel{} had signed a magical, binding contract that bound their first born \cArielsSon{\offspring}'s soul to you. \cEric{} reacted as one might expect an unhappy monarch to react. \cEric{\They} summoned \cEric{\their} guards to drag you off to the dungeons. Well, you weren't having any of that. You attacked the first guards to arrive on the scene. The delay was unfortunate however, and you ended up having to fight dozens of guards to escape. In the process, you expended a tremendous amount of magical power. You could feel the spirits lurking -- lending you power and laughing as they did. As you fought to escape the castle, your mind scrambled for an escape from this crushing, new debt. A solution appeared in the \cEric{\prince}ling's, \cSlave{\sibling}. \cSlave{\They} was a font of magical power, even on land, where magic is rare. You lunged across the battle, which had extended out onto the balcony, and knocked the \cSlave{\kid} over the edge, into the water below. You dove after \cSlave{\them}, vanishing from sight under the waves, and dragging your quarry with you.

You cast a spell to keep the \cSlave{\kid}, \cSlave{}, alive underwater, and then reached for the power to heal your wounds. To your consternation, when you reached into the aether, there was nothing there. The spirits had cut you off. You begged and pleaded with them, but they claimed that they would not extend you any more credit on the magic until you started to make payments on your existing debt. The spirits threw you off the astral plane, back into your gravely wounded body. Through the haze of pain, you realized you had to reach \cManta{}. \cManta{} was a powerful advisor in \cKing{}'s court, but \cManta{\they} wouldn't ask too many questions. \cManta{\They} had his own secrets to protect.

You don't entirely remember how you managed to stave the sharks off long enough to reach the Magician's Guild Hall, but you did. \cManta{} was indeed of great help. \cManta{\They} brewed potions to close your wounds, although he could do little to reverse the blood loss. Under your direction, which you gave in between bouts of fainting, \cManta{} also brewed a potion that would allow you to control the human \cSlave{\prince} you had just stolen. While it hurt your pride tremendously to reveal how to brew such a powerful potion, you simply had to do so. While busy over the cauldron, \cManta{} offered you some sage, if unsolicited advice: ``Play the long game.'' He didn't know exactly what you were up to, but the wounds you sustained certainly didn't come from any merperson weapon.  As a last service before \cManta{} had to return to the castle-- \cManta{\they} couldn't afford to be missed-- \cManta{} sent a sealed missive to \cPriest{}.

This whole wretched plan was cursed. You were calling in so many favors just to stay alive. \cPriest{} comes from a very powerful, very old mafia family. You had in the past helped them out by providing magical solutions to a few trickier problems and they owed you one.  With \cPriest{\their} help, you disappeared from \pAtlantis{}, with a few victims who wouldn't be missed much. You extracted their souls to begin paying back the spirits, regaining you access to magic should you need it, and soul--tapped \cSlave{} to help pay the interest on your remaining debt.

You kept a tight lid on your magic for the next 15 years, relying on \cPriest{} and his mafia connection to raise \cSlave{} up through the ranks of the Merchant's Guild. You had \cSlave{} take on the name \cSlave{\MYname}, just in case word should somehow get back to \cAriel{} and \cEric{}. Aside from giving you the legitimacy you needed to re-enter polite \pAtlantis{}n society, under the guise of ``\cWitch{\MYname}'', \cSlave{} did indeed have magic. It bloomed rapidly under the sea, and he was soon a full fledged quarent. (It is for this reason that you don't simply extract \cSlave{\their} soul for the spirits -- \cSlave{\they} is too useful, and that is saying something, given the crushing debt you've incured).

% You used \cSlave{\them} gift to learn all kinds of things about people, including \cManta{}. \cManta{}'s history was particularly interesting. According to the cards, which seldom ever lie, \cManta{} is a wayward branch of \cKing{}'s family tree. With that knowledge, a few other things started to fall into place, and you understood why \cManta{} put up with all of the bullshit at court. \cManta{\They} is trying to maneuver \cManta{\them}self into the throne. You don't particularly object -- \cManta{\they} would probably make a better \cManta{\King} than \cKing{} does -- but you won't be happy if \cManta{\they} disposes of \cKing{} before you have a chance to put your plans into action.

While you don't appreciate people lecturing you, about anything, \cManta{} did have a valid point while \cManta{\they} was treating your wounds. It was time to enter the long game. These ``get rich quick'' or to be more accurate ``get out of debt quick'' plans seem to be nothing but trouble. Your latest plan involved \cKing{\King} \cKing{}. The spells you cast on \cSlave{} worked out so well, it was high time you put them to grander use. If you could slip \cKing{} a love potion, \cKing{} would become enamored of you, and you would be able to extract his soul willingly. Souls removed unwillingly are often damaged, and therefore of much less use to the spirits. \cKing{}'s soul would be a huge payment for the spirits, and would go a long way toward clearing your debts, except for the one concerning \cAriel{}. You therefore began to leverage your connections through \cSlave{}'s role in the Merchant's Guild. Eventually you managed to secure tickets to tonight's gala at the palace. It is time to try to ensnare \cKing{}.

To your surprise, once you secured the tickets you realized that \cAriel{\King} \cAriel{} would be in attendance tonight. What\ldots{} luck. Rather than wait forever for the chance at a \cAriel{}'s \cArielsSon{\offspring}, you could have the \cAriel{\parent}'s soul now. You began to build a new amulet, this one from a shell. It needs only a few finishing touches tonight. You just need to find the \sRunicCircle{}, trace the circle in chalk, and then spend 3 minutes in uninterrupted meditation with the shell amulet in your hands.  All you need to do then is convince \cAriel{} that she can save \cAriel{\their} \cArielsSon{\offspring} by putting the amulet around her neck and wishing for \cArielsSon{\their} soul to be saved. This will trap \cAriel{} in the same kind of debt that you are trapped in. The spirits on the other side greatly appreciate new servants, and this will probably nullify much of your debts to the spirits. If you can't trick \cAriel{} into incurring \cAriel{\their} own debt to the spirits, you could get her to help you with a \gRitual{} Ritual instead.

When you arrived at the palace, there was an old man sitting at the base of the stairs, spinning a tale about the wishing stone. At first you were just going to brush past him, but you tasted magic in the water around him. The old man was more than he appeared to be. In fact, he was not at all the crazy old coot he appeared. He was a projection from the \iWishingStone{\MYname} itself. It was here, in the palace! If you could get your hands on the stone, you could wish for magical powers of your own, and forever free yourself from the spirits -- you would still owe them though. Alternately, you could wish away your debts to the spirits, and forfeit your access to magical power in exchange for a clean slate. Either way, the wish would consume the stone, but it would be totally worth it.

\begin{itemz}[Goals]
  \item Ensorcell \cKing{\King} \cKing{} via a love potion.
  \item Finish the second amulet and then trick \cAriel{} into using it to wish to spare her son.
  \item If you can't manage that, at least make \cAriel{} assist you in a \gRitual{} ritual to repay \cAriel{\their} debt.
  \item Siphon motes of soul from as many people as possible to make payments on your debt. This is a convenient way to make people pay for potions.
  \item Keep an eye on \cSlave{} and make sure he hasn't found any loopholes in the control spells.
  \item Avoid anyone discovering that you are actually \cWitch{}.
\end{itemz}

\begin{itemz}[Notes]
  \item You must be wearing your ``\iAmulet{}'' in order to do magic. If you lose the amulet, you may not use any of your abilities, or brew any potions until you regain it.
\end{itemz}

\begin{itemz}[Trivia]
  \item The Magician's Guild, despite being formally dissolved, continues to meet in secret up through the present day.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cKing{}} The current \cKing{\King} of \pAtlantis{} target of your love potion. Once \cKing{\they} is in love with you, \cKing{\they} will willingly give up \cKing{\them} soul.
  \contact{\cManta{}} A powerful magician in \cKing{}'s court. \cManta{\They} strictly regulates magic in \pAtlantis{} since \cAriel{} left.
  \contact{\cSlave{\MYname}} Secretly \cSlave{}, your slave and the representative from the Merchant's Guild at the conference.
  \contact{\cPriest{}} A useful contact in the mafia. You've done business in the past and respect \cPriest{\them} for his usefulness.
\end{contacts}

\end{document}
