\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cGeneral{}}

\updatemacro{\cSlave}{
  \nickname{Aldric}
  \mapnickinformal
}

\updatemacro{\cQueen}{
  \nickname{Athena}
  \mapnickinformal
}

You are a shape-shifting general out to protect your family and your adopted homeland.

You were born on land to a single mother. You never knew your father growing up. You took one of the few paths open to you - the military. You joined up with the \pAmerica{}n army at the age of 15 to support your mother. Your strength and wit served you well, and you rose through the ranks. By the age of 25, you made drill sergeant. It was your job to train all of the new recruits. You did so well at that job that you were also named captain of the royal guard. This brought you in fairly close contact with the royal family. You struck up somewhat of a friendship with the king, and even beat him at chess occasionally.

When the royal twins were old enough, the unenviable job of training them in swordsmanship fell to you. The boys were a pair of royal brats -- at least at first. \cEric{} outgrew this quickly enough, but \cSlave{} never did take kindly to being ordered around. You are sure that you would have eventually turned both of them into stellar soldiers and leaders if the shipwreck hadn't cut your plans short.

It was a on an expedition to the Labrador Sea with the King that an icy storm sprung up. Despite the best efforts of the seasoned crew, the ship was smashed to pieces on the coast of Greenland. You were thrown into the numbingly cold water, and lost consciousness when a wave smashed you against a rock. Your last thought was ``This is it''.

And then you woke up. At the bottom of an underwater canyon. You were bewildered for few minutes as you tried to remember what happened. Were you dead? You didn't feel dead -- everything hurt. But you were under water. You could breathe under water and for some reason you had a tail. A tail instead of legs. You were a \cGeneral{\mer}! Eventually you got over the shock and went looking for your friends and the King.

It took you 2 days to find the shipwreck, and when you did, you were heartbroken. The ship had been battered to pieces, and there were clearly no survivors. You  weighed your options and realized that you couldn't go back to \pAmerica{} with gills and a tail. You were half fish now, and didn't know if you could change back. If you did return, you would probably be treated as a traitor. Merfolk occasionally attacked ships, and it was too convenient that you, a \cGeneral{\mer}, were the only survivor.

You reluctantly looted the ship for a few valuable items and set off in search of civilization. You found a military outpost of \pAtlantis{} in the Norwegian Sea, and traded the trinkets from the ship for a chance to earn the merfolk's trust.  The constant border skirmishes with \pPacifica{} gave you plenty of opportunity to master the use of a trident. Your military training from \pAmerica{} served you well, and you were soon a trusted member of the outpost. After about a year, they allowed you to officially join the Guardian's Guild, \pAtlantis{}'s military.

You enjoyed the company of your new brethren, and often went out to bars with them, despite the fact that you were almost twice the age of some of the new recruits. Every time you would go though, in just about every bar you went to, some drunk, or the bartender himself would tell you that you looked exactly like some old drunk who used to frequent the place. Eventually, you stopped dismissing the stories, and began to wonder if there might not be something to it. In particular, you wondered if this mysterious drunk might be your father.

You took a sabbatical from the Guardian's Guild to follow the trail of drunken stories. It was a convoluted trail, and nothing was ever concrete, at least until you reached the gates of a palatial estate. You marched onto the grounds and demanded to see the Lord. The servants put up a token resistance, saying that the lord was unavailable -- clearly he was drunk. As usual apparently. Once you gained an audience with the Lord, it was clear that he was your father. There was no mistaking the resemblance. It was like looking into the future, and seeing yourself aged 20 years. Once you sobered your father up, he revealed to you the family secret. Shape-shifting. Your transformation into a \cGeneral{\mer} was totally normal. Better still, you could change back! You could be human again! -- Your elation faded a moment later, as you realized you had been gone for almost 3 years. There was no way you'd be accepted back at the palace.

Instead, you decided to build a real life here, in the North Sea. You took over the reigns of the estate, and soon restored credibility and respect to the family name. You worked prominently as a member of the Guardian's Guild, and rose through the political ranks as well, to become very well respected. You even visited the \pAtlantis{}n capital a few times. With all of the social pressures of your new life you sometimes needed a break. Once a week or so, you would swim to some abandoned beach somewhere, shape-shift into a human and sit on the beach and meditate. It felt good to cross your legs occasionally.

It was on one of these trips that you met \cQueen{}. You noticed the bouys holding up your fishing net just off shore to be moving in a very peculiar pattern. You thought a dolphin or something was caught in the net. When you went out to investigate, you found a \cQueen{\mer} caught in the net. You cut \cQueen{\them} free, and then dove after \cQueen{\them} when \cQueen{\they} took off. After you got \cQueen{} to calm down, you realized that \cQueen{\they} were indeed the \cQueen{\King} of \pAtlantis{}. To you confusion, \cQueen{\they} introduced \cQueen{\them}self as \cQueen{\MYname}. Eventually you got the whole story out of \cQueen{\them} -- or at least enough of it. \cQueen{} was running from \cQueen{\them} past as an assassin. \cQueen{} was in need of a place to hide and being the upstanding citizen you were, you offered to let \cQueen{\them} stay on your estate for a while.  Three years later, you realized that neither one of you wanted \cQueen{\them} to leave. You had fallen in love. Despite the complications should anyone discover who \cQueen{} really was, you decided to take the chance and marry \cQueen{\them}.

While your home life has vastly improved in the last couple of years, the fighting with \pPacifica{} has gotten much worse. Border skirmishes are common, and orders often come from the capital to make strikes into \pPacifica{}n territory. By now, you had been promoted to general, and so found yourself in charge of the very outpost you had encountered all those years ago when you first became a \cGeneral{\mer}. Due to the increased tension with \pPacifica{}, the outpost was expanded into a full fort. You find yourself leading nearly a hundred soldiers and trying to protect the town that has sprung up around the outpost.


\begin{itemz}[Goals]
  \item Blah
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{}
\end{contacts}

\end{document}
