\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cUrchin{}}

Grew up in a mafia family, learning that everything has a price. Ursula is an old friend of the family.

Met Ariel as a teenager, joined the explorer's guild with her and decided to walk the straight and narrow for her -joined the priesthood. You thought you were going to marry her some day.  Then she asked you if you knew a magician. You tried to dissuade her. She swore not to, but then she went anyway.

Ariel turns human and this sends you into a tailspin depression for a couple of years. You are really mad at her. You want to get even.

Your family finally contacted you again when your sister was bitten by a shape shifter. She was in a lot of pain before she died. You hate all shape shifters b/c of this.

Once you were back in the fold, you start exploiting your position as priest for the black market to acquire children. You played up the idea of children born under the full moon as being cursed, and soon had a steady, if small supply of children.

You kept up contacts in the explorer's guild too. That is when \cPlant{} approached you about taking \cPrincess{} across the border. This was a convenient way to get in with the royal family again, and a good cover for moving children into \pPacifica{}.

You are mad at \cPrincess{} for getting you caught.

\cWitch{} is alive, here and pretending to be Pearl. She is your contact for potions.

Plot of land - massive bed of pearls - your family wants exclusive access. this is going to require keeping the land in Atlantican hands.

You have a buyer for a glow shell, we just need to get one. Also you have a buyer here for a child. You need to make that exchange subtly.




\begin{itemz}[Goals]
  \item Blah
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{}
\end{contacts}

\end{document}
