\documentclass[char]{NeptuneBall}
\begin{document}
\name{\cWillow{}}

You are a \cWillow{\prince}, which is awesome, and you get to visit a whole new world, which is even awesomer!

Your life so far has been \emph{the greatest thing ever}. You love your \cAriel{\pa}, \cAriel{}, and your \cEric{\pa}, \cEric{}, and they love you too! You know because they always give you cool toys and tell you all sorts of interesting things about the world! The coolest part is that your \cAriel{\pa} used to be a \emph{\cAriel{\mer}}, and you bet \cAriel{\they} has all \emph{kinds} of cool stories to tell - if only \cAriel{\they}'d let you in on the secrets!

Well, one day, you were sneaking around, because you're good at that, and you heard you \cAriel{\pa} telling your \cEric{\pa} that \cAriel{\they} was gonna go back down under the sea! Well, of course you couldn't keep quiet about that! So you jumped right up and asked \emph{really, really} hard for them to let you come - and after a while, \cEric{\pa} said yes! You were so excited, you almost exploded!

Obviously there are a \emph{bazillion} things you wanna know about "`\pAtlantis{}"' and everywhere else under the sea, but even you know there are limits to what you can find out in one go. So, like the logical \cWillow{\prince} and future ruler that you are, you made sure to decide on a few priorities for yourself before the start of the ball.

First, make friends! Any budding \cWillow{\prince} knows that making friends means power, so you want to make as many friends as possible. They're all going to be in one place and not going anywhere, so now would be a great time! You also wanna meet your grand\cKing{\pa}, who your \cAriel{\pa} talks about a lot. \cKing{\They} sounds really nice, and maybe \cKing{\they}'ll give you presents!

Second, your \cAriel{\pa} wouldn't tell you many stories about the world under the water, but \cAriel{\they} did tell you about the dancing. You were immediately enchanted by the idea of dancing \emph{in 3D}, so while you're here, you want to learn as much about that as possible.

Third, as you were walking in here, you heard a crazy old man yelling something about a \iWishingStone{\MYname}. You don't know what that is, but it sounds super neat, so you really want to find it!

This all sounds like quite a lot of stuff to do in just four hours at the ball! Of course, if you could find some way to become a \cWillow{\mer}, then you'd have all of the time in the world, and you'd get to move in 3D \emph{all the time}. Maybe you should work on that first...

\begin{itemz}[Goals]
  \item Find some way to become a \cWillow{\mer} without letting your \cAriel{\parent} find out!
  \item Learn as many dance styles as possible.
  \item Make as many friends as possible, especially with your grand\cKing{\pa}.
	\item Find the wishing stone
  \item Find out everything ever. If you learn anything cool, go tell your \cAriel{\parent}.
\end{itemz}

%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cAriel{}} Your \cAriel{\parent}. She's here to protect you and hang out with her family.
	\contact{\cKing{}} Your grand\cKing{\parent}. He is trying to get the treaty signed.
\end{contacts}

\end{document}
