\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gBuff{}}

You have created a special potion that is unknown to other magicians. This potion causes the target's CR to increase by 2 for {\bf 10 minutes}.  You have previously conducted a ritual on yourself that causes this potion's effect to last longer on you. If you consume this potion yourself, your CR will increase by 2 for {\bf 30 minutes}. These CR buffs DO NOT stack. The target will receive a magical effect of level 4 for the duration of the potion.

This potion is administered like any other potion. In order to administer the potion, the victim must either be a willing or helpless victim, or you may stick 1 sticker on the target without their knowledge. Then go give a GM the potion packet. They will take care of the rest. If the potion is drunk directly, it takes effect immediately - but it cannot be used in response to an attack, so if you think you're being attacked, down it!

The potion is BLUE in color and takes 30 minutes to brew. 

The required ingredients are:
\begin{enumerate}
\item \iManOfWar{}
\item \iTeeth{}
\item \iSwordfish{}
\end{enumerate}

This potion is brewed as any other potion would be.\\

{\bf How to Brew a Potion:}\\ %%MAKE SIGNS!!!
\begin{enumerate}
  \item Acquire the necessary ingredients.
  \item Stand in front of an unused cauldron for one minute. At the end of this time, destroy the ingredients (they have been consumed by the potion), swap the cauldron sign to ``Full of liquid'' and write down the color of the potion you are brewing.
  \item Return after the duration listed above and stir the potion for 1 minute. Put both hands on the sign for this time.
  \item Take the appropriate potion from the envelope below the cauldron, erase the color, and swap the sign back to ``An Empty Cauldron''.
\end{enumerate}
\end{document}