\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gDance{}}

You love The \cExExKing{} Ball. It is an annual event of great beauty and culture. This year, your secret relationship with \cDiplomat{} has enamored you to the ball even more. So much so that you asked your \cKing{\parent} if you could help organize the ball. \cKing{} agreed to let you organize a dance showcase just before the banquet.

In order to make this the best, and most romantic ball ever, you've decided on an ambitious plan.  You want to have at least {\bf two couples} dance each of {\bf three  kinds} of dance at the showcase.\\

The three dances are:
\begin{enumerate}
\item Merengue, the national dance of \pAtlantis{}.
\item Cross-step waltz, the national dance of \pPacifica{}.
\item Swing, the national dance of \pAmerica{}.
\end{enumerate}

You need to get four or more people (two couples minimum) to agree to perform each dance. You do not need the same four people for all three dances, but there is also no limit to how many dances any one person can perform. You {\bf may} be one of the performers. Unfortunately you only know one dance so far. You simply must get people to teach you more.

You will have to get people to teach you, and to teach each other how to dance before the showcase at {\bf \cTOneFifty{}}. You should plan the showcase to take about 10 minutes (one song per dance type), and for the showcase to wrap up just in time for the banquet to be served. Appropriate music will be provided by the band.

Of course, you will also need an audience. Make sure people attend the showcase!

\end{document}