\documentclass[green]{NeptuneBall}
\begin{document}
\name{\gMonsterTransformation{}}

As an absolute last resort, when all is lost and you are under attack, you have the ability to turn into a giant monster. Though this form carries with it immense power, you have made only the most basic preparations, and as such, it quickly takes its toll and loses strength.

When you use your Monster Transformation ability, call a game halt and negate any combat attacks currently being used on you, \emph{including} waylays. You turn into a giant monster. Discard any red headbands that you are currently wearing and put on a black one. Your CR becomes {\bf 20}, but every time you perform any type of {\bf attack} or {\bf resist}, your CR drops by {\bf 4}. When your CR becomes 4, you no longer lose CR while attacking.


{\bf Advantages of Being a Monster:}
\begin{itemize}
\item You can resist waylays
\item You are immune to poisons
\item You no longer need a weapon to make wound attacks.
\item You do not become bloody from wounding other players
\item You treat all bulky items as 1 hand bulky.
\end{itemize}

{\bf Disadvantages of Being a Monster:}
\begin{itemize}
\item You are still unable to killing blow
\item You are immune to healing, so don't get beaten up!
\end{itemize}

{\bf Note:} Giant monsters are scarier when no one knows that they're getting weaker. Your true power is in intimidation. Consider being consistent with your attacks while attacking with less than your full CR. Don't go too low, though - performing an attack the target resists at the wrong time could be fatal to you! 

This transformation is irreversible within the scope of game, so most of your previous goals become moot. However, this form comes with a terrible price that must be repaid immediately. Tour new goal becomes to perform a ritual to pay back the spirits, then to escape the palace with your life.

\begin{description}
\item[First] Knockout or restrain a member of royalty and bring them to <the magic circle used by the magicians guild for initiations>. Once they are inside the circle, they are automatically restrained as long as you are in the room.
\item[Second] Perform a minute of chanting magical rituals, and at the end, killing blow them with a 3 count. This is the only situation in which you may killing blow anyone.
\item[Third] Escape the palace (leave game).
\end{description}

\end{document}